### 2020-07-22 eda.Rmd
Add .Rproj and recreate Table II

---
output:
  pdf_document
fontsize: 10pt 
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
knitr::opts_chunk$set(fig.width = 6)
knitr::opts_chunk$set(fig.height = 4)

options(knitr.kable.NA = "")
options(scipen = 999)

library(tidyverse)
library(haven)

```

```{r}
seed011204 <-read_stata("dataverse_files/seedanalysis_011204_1.dta")

seed080404 <- read_stata("dataverse_files/seedanalysis_080404_1.dta")

combined <- read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")

```

```{r}

combined <- combined  %>%
  # turn dollars into hundreds of dollars
  mutate(
    totbal = totbal / 100,
    newtotbal = newtotbal / 100
  ) %>%
  # fix population variable
  mutate(pop = as.numeric(str_replace(pop, ",", ""))) %>%
  # create bank penetration variable%>%
  mutate(brgy_penetration = no_clients / pop)

combined <- combined %>%
  group_by(brgy_penetration) %>%
  mutate(sd_totbal = sd(totbal),
         mean_totbal = mean(totbal)) %>%
  ungroup()

treated <- combined %>%
  filter(!is.na(treatment))

treated <- treated %>%
  # create control dummy
  mutate(control = as.numeric(group == "C")) %>%
  # create distance to bank variable
  mutate(dist_GB = 
           case_when(
             butuan == 1 ~ dbutuan,
             ampayon == 1 ~ dampayon
           )
  )

treated %>%
  group_by(group) %>%
  summarize(n(), mean(totbal), sd(totbal))

```

## Remake Table II

### Panel A.

```{r}
summary(lm(totbal ~ factor(group) - 1, data = treated))
summary(aov(totbal ~ factor(group), data = treated))

summary(lm(active ~ factor(group) - 1, data = treated))
summary(aov(active ~ factor(group), data = treated))

summary(lm(dist_GB ~ factor(group) - 1, data = treated))
summary(aov(dist_GB ~ factor(group), data = treated))

summary(lm(brgy_penetration ~ factor(group) - 1, data = treated))
summary(aov(brgy_penetration ~ factor(group), data = treated))

summary(lm(sd_totbal ~ factor(group) - 1, data = treated))
summary(aov(sd_totbal ~ factor(group), data = treated))

summary(lm(mean_totbal ~ factor(group) - 1, data = treated))
summary(aov(mean_totbal ~ factor(group), data = treated))

summary(lm(pop ~ factor(group) - 1, data = treated))
summary(aov(mean_totbal ~ factor(group), data = treated))
```

### Panel B.

```{r}
summary(lm(yearsed ~ factor(group) - 1, data = treated))
summary(aov(yearsed ~ factor(group), data = treated))

summary(lm(female ~ factor(group) - 1, data = treated))
summary(aov(female ~ factor(group), data = treated))

summary(lm(age ~ factor(group) - 1, data = treated))
summary(aov(age ~ factor(group), data = treated))

summary(lm(impatient_mon01 ~ factor(group) - 1, data = treated))
summary(aov(impatient_mon01 ~ factor(group), data = treated))

summary(lm(hyper_mon_new2 ~ factor(group) - 1, data = treated))
summary(aov(hyper_mon_new2 ~ factor(group), data = treated))

count(treated, group)
```

Questions:

1. We examine whether individuals who exhibit hyperbolic preferences in hypothetical time preference questions are more likely to open such accounts, since theoretically these individuals may have a preference for commitment. 
2. Second, we test whether such individuals save more as a result of opening the account.

Our questions:

* Remake table 2 with non-parametric standard errors
* Remake table 3 (meh)
* Remake table 6
* Remake table 7

* Did the respondents make positive savings?
* What proportion of people opened the account?
* Did the treatment group save more than the control group?
* estimate the pdf of savings and then estimate the percentiles

```{r}
count(combined, group)

```

### 2020-07-22 eda.Rmd
Remake Table VII

@@
 library(haven)
-
+library(quantreg)
 ```
@@
 ```{r}
-
 combined <- combined  %>%
@@
 combined <- combined %>%
+  # calculate the mean and sd for each bank
+  # the Stata code is a little cyptic
   group_by(brgy_penetration) %>%
@@
 
+# create a set with the 1777 observations that are in the SEED, 
+# marketing treatment, or control group
 treated <- combined %>%
@@
 
-Questions:
+## Remake Table VII
+
+```{r}
+rq(as.numeric(balchange) ~ treatment + marketing, 
+   tau = seq(from = 0.1, to = 0.9, by = 0.1),
+   data = filter(seed011204, !is.na(treatment)))
+
+rq(as.numeric(balchange) ~ treatment + marketing, 
+   tau = seq(from = 0.1, to = 0.9, by = 0.1),
+   data = treated)
+```
+
+## Questions
+
+* Remake table 6 with bootstrapped standard errors
+* Remake table 7 with kernel density estimators and compare with the percentiles percentiles from the quantile regression
+* Estimate the proportion of people who would open an account
+* Do a k-sample test to compare the savings or change in svaings of the three groups. Then do pair-wise tests with corrections for multiple testing. 
+* We can use LOESS/KDE to compare any of the bivariate relationships
+    * Year of education by totbal or change in totbal
+    * Age or age2 by totbal or change in totbal
 
@@
 2. Second, we test whether such individuals save more as a result of opening the account.
-
-Our questions:
-
-* Remake table 2 with non-parametric standard errors
-* Remake table 3 (meh)
-* Remake table 6
-* Remake table 7
-
-* Did the respondents make positive savings?
-* What proportion of people opened the account?
-* Did the treatment group save more than the control group?
-* estimate the pdf of savings and then estimate the percentiles
-
-```{r}
-count(combined, group)
-
-```

### 2020-07-22 eda.Rmd
Update before last class

@@
 
-* Remake table 6 with bootstrapped standard errors
+* Remake table 6 with nonparametric regression techniques. To deal with outliers, they do a bunch of probits for specific thresholds. 
 * Remake table 7 with kernel density estimators and compare with the percentiles percentiles from the quantile regression

### 2020-07-23 draft.Rmd
Add draft template and references.

---
header-includes:
   - \usepackage{ulem}
   - \usepackage{float}
   - \usepackage{algorithm}
   - \usepackage{algorithmic}
output:
  pdf_document
fontsize: 10pt 
editor_options: 
  chunk_output_type: console
bibliography: references.bib  
---

```{r rmarkdown-setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
knitr::opts_chunk$set(fig.width = 6)
knitr::opts_chunk$set(fig.height = 4)

options(knitr.kable.NA = "")
options(scipen = 999)
```

# Commitment Savings Devices

## 1. Introduction

## 2. Summary of Data for Analysis

## 3. Paired Comparisons

### 3.1 Methods

### 3.2 Results

### 3.3 Discussion of Results

## 4. Two-sample Test and K-Sample Test

### 4.1 Methods

### 4.2 Results

### 4.3 Discussion of Results

## 5. Robust Regression

### 5.1 Methods

### 5.2 Results

### 5.3 Discussion of Results

## Conclusion

\newpage

## Appendix

```{r ref.label = knitr::all_labels(), echo = TRUE, eval = FALSE}
```

## References

### 2020-07-25 draft.Rmd

@@
 options(scipen = 999)
+
+```
+
+```{r r-setup}
+library(tidyverse)
+library(haven)
+
+```
+
+```{r load-data}
+seed011204 <-read_stata("dataverse_files/seedanalysis_011204_1.dta")
+
+seed080404 <- read_stata("dataverse_files/seedanalysis_080404_1.dta")
+
+combined <- read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")
+
+```
+
+```{r data-cleaning}
+# this cleaning is based on Stata scripts from the original Authors' code
+
+combined <- combined  %>%
+  # turn dollars into hundreds of dollars
+  mutate(
+    totbal = totbal / 100,
+    newtotbal = newtotbal / 100
+  ) %>%
+  # fix population variable
+  mutate(pop = as.numeric(str_replace(pop, ",", ""))) %>%
+  # create bank penetration variable%>%
+  mutate(brgy_penetration = no_clients / pop)
+
+combined <- combined %>%
+  # calculate the mean and sd for each bank
+  # the Stata code is a little cyptic
+  group_by(brgy_penetration) %>%
+  mutate(sd_totbal = sd(totbal),
+         mean_totbal = mean(totbal)) %>%
+  ungroup()
+
+combined <- combined %>%
+  # create control dummy
+  mutate(control = as.numeric(group == "C")) %>%
+  # create distance to bank variable
+  mutate(dist_GB = 
+           case_when(
+             butuan == 1 ~ dbutuan,
+             ampayon == 1 ~ dampayon
+           )
+  )
+
+# create a set with the 1777 observations that are in the SEED, 
+# marketing treatment, or control group
+treated <- combined %>%
+  filter(!is.na(treatment))
+
 ```

### 2020-07-25 draft.Rmd
Conduct a Paired Wilcoxon Rank-Sign test on the SEED accounts

@@
 ```{r load-data}
-seed011204 <-read_stata("dataverse_files/seedanalysis_011204_1.dta")
+seed011204 <-read_stata("dataverse_files/seedanalysis_011204.dta")
 
-seed080404 <- read_stata("dataverse_files/seedanalysis_080404_1.dta")
+seed080404 <- read_stata("dataverse_files/seedanalysis_080404.dta")
 
-combined <- read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")
+combined <- read_stata("dataverse_files/seedanalysis_011204_080404.dta")
 
@@
 
+```{r, }
+seed_accounts = treated %>% filter(treatment == 1)
+hist(seed_accounts$balchange,
+     main="Histogram of balance changes for SEED accounts",
+     xlab="Balance Change")
+
+filtered_seeds = seed_accounts %>% filter(balchange <=10000)
+hist(filtered_seeds$balchange,
+     main="Outliers removed balance changes for SEED accounts",
+     xlab="Balance Change")
+
+print("Summary statistics for Seed account balance changes")
+summary(seed_accounts$balchange)
+```
+
 ## 3. Paired Comparisons
@@
 
+We will use a one sided Wilcoxon Signed-Rank Test at a significance of $\alpha=0.05$ to test if the the savings of customers with SEED accounts increased.
+
+We will be testing the following hypothesis where $\theta_d$ is the mean of the differences in savings for customers with SEED accounts from before and after the trial
+
+$H_0: \theta_d = 0$
+
+$H_a: \theta_d >0$
+
+We will be used a Signed-Rank test given the significant outliers in the data.
+
+The Wilcoxon Signed-Rank Test statistic is done by ranking the absolute values of the paired differences.
+The ranks are then signed positive or negative based on whether or not the corresponding differences are positive or negative.
+The test statistic is the sum of the positive ranks.
+As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with $E(SR_+) = \frac{n(n+1)}{4} = 177451.5$ and $\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=299005778$.
+[@Higgins]
+
 ### 3.2 Results
 
+```{r, echo=FALSE}
+wilcox.test(seed_accounts$totbal, seed_accounts$balchange,alternative = "greater", paired=TRUE)
+
+```
+
 ### 3.3 Discussion of Results
+
+As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternate hypothesis.
+We conclude that customers who had SEED accounts saw an increase in savings over the duration of the trial.
+It is worth noting that we have not yet shown that the SEED accounts are more effective savings accounts than other methods, just that customers were able to save with them.
 

### 2020-07-25 draft.Rmd
Draft regression section

--- 2020-07-25 draft.Rmd
@@
 library(tidyverse)
-library(haven)
+library(haven) # reading Stata data
+library(MASS) # M-estimation
+library(Rfit) # rank-based regression
+library(patchwork)
+library(broom)
+library(sandwich)
+library(lmtest)
 
@@
 combined <- read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")
+
+six_months <- filter(seed011204, !is.na(treatment))
 
@@
   # calculate the mean and sd for each bank
-  # the Stata code is a little cyptic
+  # the Stata code is a little cryptic
   group_by(brgy_penetration) %>%
@@
 
+[@Ashraf2006] estimate regression models with change in savings account balance as the dependent variable and the different treatments and controls as independent variables.
+This is to estimate the intent-to-treat effect (ITT) of the commitment savings account--that is the effect on account balances of being offered the commitment savings account versus not being offered the account or being offered the marketing treatment instead.
+
+The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months.
+Accordingly, the dependent variable is not approximately normally distributed and the error term of their estimated models is not approximately normally distributed.
+
+```{r}
+skewa <- six_months %>%
+  ggplot(aes(balchange)) +
+  geom_density() +
+  scale_x_continuous(labels = scales::comma) +
+  scale_y_continuous(limits = c(0, 0.004)) +
+  labs(title = "The Dependent Variables Are Highly Right Skewed",
+       subtitle = "Six Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",       
+       y = NULL) +
+  theme_minimal()
+
+skewb <- treated %>%
+  ggplot(aes(balchange)) +
+  geom_density() +
+  scale_x_continuous(labels = scales::comma) +
+  scale_y_continuous(limits = c(0, 0.004)) +
+  labs(title = "",
+       subtitle = "Twelve Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal()
+
+skewa + skewb
+
+rm(skewa, skewb)
+
+```
+
+The SEED treatment, the marketing control, and the full control all have outliers. Though the SEED treatment's outliers are distinct for the change in twelve month balance.
+
+```{r}
+skewa <- six_months %>%
+  ggplot(aes(balchange, y = group, color = group)) +
+  geom_point(alpha = 0.2) +
+  scale_x_continuous(labels = scales::comma) +
+  labs(title = "The Dependent Variables Are Highly Right Skewed",
+       subtitle = "Six Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",       
+       y = NULL) +
+  theme_minimal() +
+  guides(color = FALSE)
+
+skewb <- treated %>%
+  ggplot(aes(balchange, y = group, color = group)) +
+  geom_point(alpha = 0.2) +
+  scale_x_continuous(labels = scales::comma) +
+  labs(title = "",
+       subtitle = "Twelve Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal() +
+  guides(color = FALSE)
+
+skewa + skewb
+
+rm(skewa, skewb)
+
+# measure of outliers from 611?
+
+```
+
+[@Ashraf2006] found only modest evidence for a statistically significant intent-to-treat (ITT) effect for the commitment savings accounts using ordinary least squares regression (OLS).
+Furthermore, they found that the differential effect of being offered the commitment savings product beyond being offered only a marketing treatment was indistinguishable from zero.
+
+The authors state:
+
+> The statistical insignificance masks the heterogeneity in the impact of the commitment treatment relative to the marketing treatment throughout the distribution of the change in balance variable.
+Using measures that minimize the influence of outliers, e.g., the probability of a savings increase and the quantile regressions below, we find a significant commitment-treatment effect relative to the marketing treatment.
+
+To deal with outliers, the authors constructed two binary outcome variables: 
+\begin{itemize}
+  \item 1 if the savings is positive and 0 otherwise. 
+  \item 1 if the savings increases by more than 20 percent and 0 otherwise. 
+\end{itemize}
+
+The authors then estimate probit models on the twelve month data and find statistically significant treatment effects.
+
+We first explore their constructed variables and then we offer an alternative approach.
+A closer look at the data show that many balances decreased or remained the same and only a fraction of balances increased after twelve months.
+
+```{r}
+# 12 months 
+treated <-  treated %>%
+  mutate(change =
+           case_when(
+             balchange > 0 ~ "Increase",
+             balchange == 0 ~ "No Change",
+             balchange < 0 ~ "Decrease"
+           )
+  ) %>%
+  mutate(change = factor(change, levels = c("Decrease", "No Change", "Increase")))
+
+count(treated, change) %>%
+  knitr::kable(caption = "Change in Balance After Twelve Months")
+
+```
+
+Importantly, inside the treatment group, more balances decreased than increased in the 12 month window.
+
+```{r}
+count(treated, group, change) %>%
+  knitr::kable(caption = "Change in Balance After Twelve Months by Treatment Group")
+```
+
+The story is even more dramatic for the 20 percent increase outcome variable.
+
+```{r}
+
+count(treated, frac_change_20) %>%
+  knitr::kable(caption = "20+% Change in Balance After Twelve Months")
+
+count(treated, group, frac_change_20) %>%
+  knitr::kable(caption = "20+% Change in Balance After Twelve Months")
+```
+
 ### 5.1 Methods
+
+We offer an alternative approach to dealing with outliers from the nonparametric statistical literature.
+
+Ordinary least squares regression estimates coefficients, $\vec{\hat{\beta}}$, that minimize the sum of squared residuals
+
+$$\min_{\vec{\hat{\beta}}} \sum_{i = 1}^N (Y_i - \hat{Y_i})^2$$
+
+The square in this optimization gives extra weight to outliers.
+In this case, all of the outliers are positive and the squared term will result in an estimated intercept and estimated coefficients that are further from zero in the positive direction.
+
+Regression with M-estimation estimates coefficients, $\vec{\hat{\beta}}$, that minimize standardized residuals where outliers receive less weight
+
+todo(aaron): citation
+
+$$\min_{\vec{\hat{\beta}}} \sum_{i = 1}^N \rho\left(\frac{Y_i - \hat{Y_i}}{\hat{\sigma}_i}\right)$$
+
+Where $\rho(x)$ is a symmetric function with a unique minimum at $x = 0$ and $\hat{\sigma}$ is an estimate of the standard deviation of the residuals.
+We use Tukey's bisquare function for $\rho$ such that
+
+$$\rho(x) = \begin{cases}
+\left(\frac{x}{c}\right)^6  - 3\left(\frac{x}{c}\right)^4 + 3\left(\frac{x}{c}\right)^2,  &  |x| \leq c\\
+1, & |x| > c
+\end{cases}$$
+
+with $c = 4.685$.
+
+Robust and rank-based regression addresses the issues of OLS outlined above by estimating coefficients, $\vec{\hat{\beta}}$, that minimize the sum of errors weighted by rank scores.
+
+The Jaeckel-Hettmansperger-McKean (JHM) estimates of the coefficients $\beta_1, \beta_2, ..., \beta_k$ minimizes
+
+$$D_j(\mathbf{Y} - \mathbf{X}\vec{\beta}) = \frac{\sqrt{12}}{(n + 1)}\sum_{i = 1}^n \left[R_i(\vec{\beta}) - \frac{n + 1}{2})\right](Y_i - \mathbf{x'}_i\vec{\beta})$$
+
+Like [@Ashraf2006], we estimate the intent-to-treat (ITT) effect with the change in balance as the dependent variable and the different treatments as the independent variables.
+Only we use M-Estimation and Robust and rank-based regression.
 
@@
 
+We begin by recreating half of Table VI from [@Ashraf2006].
+All models are estimated using ordinary least squares regression and the standard errors are HC1 heteroskedasticity-robust standard errors [@MacKinnon1985].
+
+```{r results = "asis"}
+six_months <- filter(seed011204, !is.na(treatment))
+
+# column 1
+lm1 <- lm(balchange ~ treatment + marketing, data = six_months) 
+se1 <- lm1 %>% coeftest(vcov = vcovHC(., type="HC1"))
+
+# column 2
+lm2 <- lm(balchange ~ treatment, 
+          data = filter(six_months, group %in% c("M", "T"))) 
+se2 <- lm2 %>% coeftest(vcov = vcovHC(., type="HC1"))
+
+# column 3
+lm3 <- lm(balchange ~ treatment + marketing, data = treated) 
+se3 <- lm3 %>% coeftest(vcov = vcovHC(., type="HC1"))
+
+# column 4
+lm4 <- lm(balchange ~ treatment, 
+          data = filter(treated, group %in% c("M", "T"))) 
+se4 <- lm4 %>% coeftest(vcov = vcovHC(., type="HC1"))
+
+stargazer::stargazer(lm1, lm2, lm3, lm4,
+                     se = list(se1[, 2], se2[, 2], se3[, 2], se4[, 2]),
+                     header = FALSE,
+                     column.separate = c(2, 2),
+                     column.labels = c("6 months", "12 months"), 
+                     omit.stat = c("adj.rsq", "rsq", "f", "ser"),
+                     title = "OLS Model")
+
+```
+
+M-estimation leads to results that look very different than [@Ashraf2006].
+Column (1) shows the change in balance after six months including all observations.
+The coefficients estimate the additional savings of the corresponding treatment over the control group.
+Column (2) shows the change in balance after six months using only the commitment savings group and the marketing group.
+Column (3) is similar to column (1), only it uses the twelve month change in balance.
+Likewise, column (4) is similar to column (2), only it uses the twelve month change in balance.
+
+In all four cases the estimated intercept is negative and the coefficients, while positive, are smaller in magnitude than the OLS model.
+That means the conditional means for the commitment savings group, the marketing control group, and the control group are all negative.
+That said, the estimated intent-to-treat effect is statistically significantly different in three of the four specifications.
+However, the treatment effects are very small.
+
+```{r results = "asis"}
+# column 1
+m_model1 <- rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = six_months)
+
+# column 2
+m_model2 <- rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
+    data = filter(six_months, group %in% c("M", "T")))
+
+# column 3
+m_model3 <- rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = treated)
+
+# column 4
+m_model4 <- rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
+    data = filter(treated, group %in% c("M", "T")))
+
+stargazer::stargazer(m_model1, m_model2, m_model3, m_model4,
+                     header = FALSE,
+                     column.separate = c(2, 2),
+                     column.labels = c("6 months", "12 months"), 
+                     omit.stat = "ser",
+                     title = "M-Estimation Model")
+
+```
+
+Robust and rank-based regression leads to results that look very different than [@Ashraf2006].
+Column (1) shows the change in balance after six months including all observations.
+The coefficients estimate the additional savings of the corresponding treatment over the control group.
+Column (2) shows the change in balance after six months using only the commitment savings group and the marketing group.
+Column (3) is similar to column (1), only it uses the twelve month change in balance.
+Likewise, column (4) is similar to column (2), only it uses the twelve month change in balance.
+
+```{r results = "asis"}
+# column 1
+rank_model1 <- rfit(balchange ~ treatment + marketing, data = six_months)
+
+# column 2
+rank_model2 <- rfit(balchange ~ treatment, 
+     data = filter(six_months, group %in% c("M", "T")))
+
+# column 3
+rank_model3 <- rfit(balchange ~ treatment + marketing, data = treated)
+
+# column 4
+rank_model4 <- rfit(balchange ~ treatment, 
+     data = filter(treated, group %in% c("M", "T")))
+
+stargazer::stargazer(
+  m_model1, m_model2, m_model3, m_model4,
+  coef = list(coef(rank_model1), coef(rank_model2), coef(rank_model3), coef(rank_model4)),
+  se = list(coef(summary(rank_model1))[, 2],
+            coef(summary(rank_model2))[, 2],
+            coef(summary(rank_model3))[, 2],
+            coef(summary(rank_model4))[, 2]),
+  header = FALSE,
+  column.separate = c(2, 2),
+  column.labels = c("6 months", "12 months"), 
+  omit.stat = c("adj.rsq", "rsq", "f", "ser"),
+  title = "Rank-based robust regression model"
+)
+
+```
+
 ### 5.3 Discussion of Results
+
+M-estimation and robust rank-based regression lead to very different results than ordinary least squares.
+
+The weight of the positive outliers leads to a positive estimated intercept and larger estimated coefficients for the treatments in the OLS model.
+The other two models, which are more robust to outliers, have negative estimated intercepts and estimated coefficients for the treatments that are much closer to zero.
+
+The skewed distribution and outliers lead to dramatically larger standard errors and confidence intervals for the OLS model than the two models that are robust to outliers.
+Interestingly, this means that more coefficients are statistically significant with M-estimation and robust rank-based regression than with OLS regression even though the effect sizes are much smaller.
+While the intent-to-treat effect is statistically significantly different than zero, the effect sizes are so small that the practical effect is
+
+The following data  compares the estimated coefficients and confidence intervals from column (3) for all three model types.
+
+```{r}
+lm3 <- lm(balchange ~ treatment + marketing, data = treated) %>%
+  coeftest(vcov = vcovHC(., type="HC1"))
+
+coefficients <- bind_rows(
+  tibble(
+    model = "OLS Model",
+    tidy(lm3)
+  ),
+  tibble(
+    model = "M Model",
+    tidy(m_model3)
+  ),
+  tibble(
+    model = "Rank-Based\nModel",
+    term = c("(Intercept)", "treatment", "marketing"),
+    estimate = rank_model3$coefficients,
+    std.error = coef(summary(rank_model3))[, 2]
+  )
+)
+
+coefficients %>%
+  mutate(conf.low = estimate - qnorm(0.025) * std.error,
+         conf.high = estimate + qnorm(0.025) * std.error) %>%
+  mutate(model = factor(model, levels = c("Rank-Based\nModel", "M Model", "OLS Model"))) %>%
+  ggplot(aes(x = estimate, 
+             y = model,
+             xmin = conf.low,
+             xmax = conf.high,
+             color = model)) +
+  geom_pointrange() +
+  geom_vline(xintercept = 0, alpha = 0.5) +
+  facet_wrap(~term, scales = "free_x") +
+  labs(title = "Model Choice Affects Estimated Coefficients",
+       x = "Estimated Beta and 95% Confidence Interval",
+       y = NULL) +
+  theme_bw() +
+  theme(legend.position = "top")
+
+```
+
+The following data visualization compares the estimated coefficients and confidence intervals from column (4) for all three model types.
+
+```{r}
+lm4 <- lm(balchange ~ treatment, 
+   data = filter(treated, group %in% c("M", "T"))) %>%
+  coeftest(vcov = vcovHC(., type="HC1"))
+
+coefficients <- bind_rows(
+  tibble(
+    model = "OLS Model",
+    tidy(lm4)
+  ),
+  tibble(
+    model = "M Model",
+    tidy(m_model4)
+  ),
+  tibble(
+    model = "Rank-Based\nModel",
+    term = c("(Intercept)", "treatment"),
+    estimate = rank_model4$coefficients,
+    std.error = coef(summary(rank_model4))[, 2]
+  )
+)
+
+coefficients %>%
+  mutate(conf.low = estimate - qnorm(0.025) * std.error,
+         conf.high = estimate + qnorm(0.025) * std.error) %>%
+  mutate(model = factor(model, levels = c("Rank-Based\nModel", "M Model", "OLS Model"))) %>%
+  ggplot(aes(x = estimate, 
+             y = model,
+             xmin = conf.low,
+             xmax = conf.high,
+             color = model)) +
+  geom_pointrange() +
+  geom_vline(xintercept = 0, alpha = 0.5) +
+  facet_wrap(~term, scales = "free_x") +
+  labs(title = "Model Choice Affects Estimated Coefficients",
+       x = "Estimated Beta and 95% Confidence Interval",
+       y = NULL) +
+  theme_bw() +
+  theme(legend.position = "top")
+
+```
 

### 2020-07-25 eda.Rmd
Draft regression section

@@
 library(quantreg)
+library(sandwich)
+library(lmtest)
+
 ```
@@
   )
-
-treated %>%
-  group_by(group) %>%
-  summarize(n(), mean(totbal), sd(totbal))
 
@@
 
+## Remake Table VI
+
+```{r}
+six_months <- filter(seed011204, !is.na(treatment))
+
+# column 1
+lm(balchange ~ treatment + marketing, data = six_months) %>%
+  coeftest(vcov = vcovHC(., type="HC1"))
+
+# column 2
+lm(balchange ~ treatment, 
+   data = filter(six_months, group %in% c("M", "T"))) %>%
+  coeftest(vcov = vcovHC(., type="HC1"))
+
+# column 3
+lm(balchange ~ treatment + marketing, data = treated) %>%
+  coeftest(vcov = vcovHC(., type="HC1"))
+
+# column 4
+boom <- lm(balchange ~ treatment, 
+   data = filter(treated, group %in% c("M", "T"))) %>%
+  coeftest(vcov = vcovHC(., type="HC1"))
+
+# The R^2 values are really zero. And the p-values for the F statistics are large
+
+```
+
 ## Remake Table VII

### 2020-07-25 draft.Rmd
Edit some typos and add more comments to the R code

@@
 ```{r}
+#
+# Create a plot to show the skew of balchange
+#
 skewa <- six_months %>%
@@
 ```{r}
+#
+# Create a plot to show the skew of balchange by group
+#
 skewa <- six_months %>%
@@
 ```{r}
-# 12 months 
+#
+# Count the types of change in balchange
+# 
 treated <-  treated %>%
@@
   knitr::kable(caption = "Change in Balance After Twelve Months by Treatment Group")
+
 ```
@@
 ```{r}
-
 count(treated, frac_change_20) %>%
@@
   knitr::kable(caption = "20+% Change in Balance After Twelve Months")
+
 ```
@@
 ```{r results = "asis"}
+#
+# OLS model
+#
 six_months <- filter(seed011204, !is.na(treatment))
@@
 
-M-estimation leads to results that look very different than [@Ashraf2006].
+We estimate identical specifications to [@Ashraf2006] using M-estimation.
 Column (1) shows the change in balance after six months including all observations.
@@
 
-In all four cases the estimated intercept is negative and the coefficients, while positive, are smaller in magnitude than the OLS model.
-That means the conditional means for the commitment savings group, the marketing control group, and the control group are all negative.
-That said, the estimated intent-to-treat effect is statistically significantly different in three of the four specifications.
-However, the treatment effects are very small.
+```{r results = "asis"}
+#
+# M-Estimation model
+#
 
-```{r results = "asis"}
 # column 1
@@
 
-Robust and rank-based regression leads to results that look very different than [@Ashraf2006].
+We estimate identical specifications to [@Ashraf2006] using robust and rank-based regressions.
 Column (1) shows the change in balance after six months including all observations.
@@
 ```{r results = "asis"}
+#
+# Robust and rank-based regression
+#
+
 # column 1
@@
 The other two models, which are more robust to outliers, have negative estimated intercepts and estimated coefficients for the treatments that are much closer to zero.
+For M-estimation and robust ranked based regression, the estimated intercepts are negative and the coefficients, while positive, are smaller in magnitude than the OLS model.
+That means the conditional means for the commitment savings group, the marketing control group, and the control group are all negative.
 
@@
 ```{r}
+#
+# Visualize column (3)
+#
+
 lm3 <- lm(balchange ~ treatment + marketing, data = treated) %>%
@@
 ```{r}
+#
+# Visualize column (4)
+#
+
 lm4 <- lm(balchange ~ treatment, 

### 2020-07-25 draft.Rmd
Switch assignment operators to equals signs

@@
 ```{r load-data}
-seed011204 <-read_stata("dataverse_files/seedanalysis_011204_1.dta")
+seed011204 =read_stata("dataverse_files/seedanalysis_011204_1.dta")
 
-seed080404 <- read_stata("dataverse_files/seedanalysis_080404_1.dta")
+seed080404 = read_stata("dataverse_files/seedanalysis_080404_1.dta")
 
-combined <- read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")
+combined = read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")
 
-six_months <- filter(seed011204, !is.na(treatment))
+six_months = filter(seed011204, !is.na(treatment))
 
@@
 
-combined <- combined  %>%
+combined = combined  %>%
   # turn dollars into hundreds of dollars
@@
 
-combined <- combined %>%
+combined = combined %>%
   # calculate the mean and sd for each bank
@@
 
-combined <- combined %>%
+combined = combined %>%
   # create control dummy
@@
 # marketing treatment, or control group
-treated <- combined %>%
+treated = combined %>%
   filter(!is.na(treatment))
@@
 #
-skewa <- six_months %>%
+skewa = six_months %>%
   ggplot(aes(balchange)) +
@@
 
-skewb <- treated %>%
+skewb = treated %>%
   ggplot(aes(balchange)) +
@@
 #
-skewa <- six_months %>%
+skewa = six_months %>%
   ggplot(aes(balchange, y = group, color = group)) +
@@
 
-skewb <- treated %>%
+skewb = treated %>%
   ggplot(aes(balchange, y = group, color = group)) +
@@
 # 
-treated <-  treated %>%
+treated =  treated %>%
   mutate(change =
@@
 #
-six_months <- filter(seed011204, !is.na(treatment))
+six_months = filter(seed011204, !is.na(treatment))
 
 # column 1
-lm1 <- lm(balchange ~ treatment + marketing, data = six_months) 
-se1 <- lm1 %>% coeftest(vcov = vcovHC(., type="HC1"))
+lm1 = lm(balchange ~ treatment + marketing, data = six_months) 
+se1 = lm1 %>% coeftest(vcov = vcovHC(., type="HC1"))
 
 # column 2
-lm2 <- lm(balchange ~ treatment, 
+lm2 = lm(balchange ~ treatment, 
          data = filter(six_months, group %in% c("M", "T"))) 
-se2 <- lm2 %>% coeftest(vcov = vcovHC(., type="HC1"))
+se2 = lm2 %>% coeftest(vcov = vcovHC(., type="HC1"))
 
 # column 3
-lm3 <- lm(balchange ~ treatment + marketing, data = treated) 
-se3 <- lm3 %>% coeftest(vcov = vcovHC(., type="HC1"))
+lm3 = lm(balchange ~ treatment + marketing, data = treated) 
+se3 = lm3 %>% coeftest(vcov = vcovHC(., type="HC1"))
 
 # column 4
-lm4 <- lm(balchange ~ treatment, 
+lm4 = lm(balchange ~ treatment, 
          data = filter(treated, group %in% c("M", "T"))) 
-se4 <- lm4 %>% coeftest(vcov = vcovHC(., type="HC1"))
+se4 = lm4 %>% coeftest(vcov = vcovHC(., type="HC1"))
 
@@
 # column 1
-m_model1 <- rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = six_months)
+m_model1 = rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = six_months)
 
 # column 2
-m_model2 <- rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
+m_model2 = rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
                data = filter(six_months, group %in% c("M", "T")))
@@
 # column 3
-m_model3 <- rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = treated)
+m_model3 = rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = treated)
 
 # column 4
-m_model4 <- rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
+m_model4 = rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
                data = filter(treated, group %in% c("M", "T")))
@@
 # column 1
-rank_model1 <- rfit(balchange ~ treatment + marketing, data = six_months)
+rank_model1 = rfit(balchange ~ treatment + marketing, data = six_months)
 
 # column 2
-rank_model2 <- rfit(balchange ~ treatment, 
+rank_model2 = rfit(balchange ~ treatment, 
                    data = filter(six_months, group %in% c("M", "T")))
@@
 # column 3
-rank_model3 <- rfit(balchange ~ treatment + marketing, data = treated)
+rank_model3 = rfit(balchange ~ treatment + marketing, data = treated)
 
 # column 4
-rank_model4 <- rfit(balchange ~ treatment, 
+rank_model4 = rfit(balchange ~ treatment, 
                    data = filter(treated, group %in% c("M", "T")))
@@
 
-lm3 <- lm(balchange ~ treatment + marketing, data = treated) %>%
+lm3 = lm(balchange ~ treatment + marketing, data = treated) %>%
   coeftest(vcov = vcovHC(., type="HC1"))
 
-coefficients <- bind_rows(
+coefficients = bind_rows(
   tibble(
@@
 
-lm4 <- lm(balchange ~ treatment, 
+lm4 = lm(balchange ~ treatment, 
          data = filter(treated, group %in% c("M", "T"))) %>%
@@
 
-coefficients <- bind_rows(
+coefficients = bind_rows(
   tibble(

### 2020-07-25 draft.Rmd
Respond to Luke's first edits

@@
 count(treated, change) %>%
+  pivot_wider(names_from = change,
+              values_from = n) %>%
   knitr::kable(caption = "Change in Balance After Twelve Months")
@@
 count(treated, group, change) %>%
+  pivot_wider(names_from = change,
+              values_from = n) %>%
   knitr::kable(caption = "Change in Balance After Twelve Months by Treatment Group")
@@
 count(treated, frac_change_20) %>%
+  pivot_wider(names_from = frac_change_20,
+              values_from = n) %>%
+  rename(`20%+ Increase` = `1`,
+         `<20% Increase` = `0`) %>%
   knitr::kable(caption = "20+% Change in Balance After Twelve Months")
@@
 count(treated, group, frac_change_20) %>%
+  pivot_wider(names_from = frac_change_20,
+              values_from = n) %>%  
+  rename(`20%+ Increase` = `1`,
+         `<20% Increase` = `0`) %>%  
   knitr::kable(caption = "20+% Change in Balance After Twelve Months")
@@
 Interestingly, this means that more coefficients are statistically significant with M-estimation and robust rank-based regression than with OLS regression even though the effect sizes are much smaller.
-While the intent-to-treat effect is statistically significantly different than zero, the effect sizes are so small that the practical effect is
+While the intent-to-treat effect is statistically significantly different than zero, the effect sizes are so small that the practical significance is limited.
 

### 2020-07-26 draft.Rmd

@@
 ```{r load-data}
-seed011204 =read_stata("dataverse_files/seedanalysis_011204_1.dta")
+seed011204 <-read_stata("dataverse_files/seedanalysis_011204.dta")
 
-seed080404 = read_stata("dataverse_files/seedanalysis_080404_1.dta")
+seed080404 <- read_stata("dataverse_files/seedanalysis_080404.dta")
 
-combined = read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")
-
-six_months = filter(seed011204, !is.na(treatment))
+combined <- read_stata("dataverse_files/seedanalysis_011204_080404.dta")
 
@@
 
+We will use a one sided Wilcoxon Signed-Rank Test at a significance of $\alpha=0.05$ to test if the the savings of customers with SEED accounts increased.
+
+We will be testing the following hypothesis where $\theta_d$ is the mean of the differences in savings for customers with SEED accounts from before and after the trial
+
+$H_0: \theta_d = 0$
+
+$H_a: \theta_d >0$
+
+We will be used a Signed-Rank test given the significant outliers in the data.
+
+The Wilcoxon Signed-Rank Test statistic is done by ranking the absolute values of the paired differences.
+The ranks are then signed positive or negative based on whether or not the corresponding differences are positive or negative.
+The test statistic is the sum of the positive ranks.
+As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with $E(SR_+) = \frac{n(n+1)}{4} = `r (842 * (842 + 1)) / 4`$ and $\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=299005778$.
+[@Higgins]
+
 ### 3.2 Results
 
+```{r, echo=FALSE}
+wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)
+
+```
+
 ### 3.3 Discussion of Results
+
+As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternate hypothesis.
+We conclude that customers who had SEED accounts saw an increase in savings over the duration of the trial.
+It is worth noting that we have not yet shown that the SEED accounts are more effective savings accounts than other methods, just that customers were able to save with them.
 

### 2020-07-26 draft.Rmd
removed echo, added inline R

@@
 ```{r load-data}
-seed011204 <-read_stata("dataverse_files/seedanalysis_011204.dta")
+seed011204 = read_stata("dataverse_files/seedanalysis_011204.dta")
 
-seed080404 <- read_stata("dataverse_files/seedanalysis_080404.dta")
+seed080404 = read_stata("dataverse_files/seedanalysis_080404.dta")
 
-combined <- read_stata("dataverse_files/seedanalysis_011204_080404.dta")
+combined = read_stata("dataverse_files/seedanalysis_011204_080404.dta")
+
+six_months = filter(seed011204, !is.na(treatment))
 
@@
 
-```{r, }
+```{r}
 seed_accounts = treated %>% filter(treatment == 1)
@@
 The test statistic is the sum of the positive ranks.
-As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with $E(SR_+) = \frac{n(n+1)}{4} = `r (842 * (842 + 1)) / 4`$ and $\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=299005778$.
-[@Higgins]
+As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with
+$E(SR_+) = \frac{n(n+1)}{4} = `r (842 * (842 + 1)) / 4`$ and 
+$\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=`r (842 * (842 + 1) * (2 * 842 + 1) / 24)`$. [@Higgins]
 
@@
 
-```{r, echo=FALSE}
+```{r}
 wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)

### 2020-07-26 draft.Rmd
run JT test

@@
 library(lmtest)
+library(NSM3)
 
@@
 
+```{r k-sample JT test}
+
+seed_balchange = seed_accounts$balchange
+marketing_balchange = (treated %>% filter(marketing==1))$balchange
+control_balchange = (treated %>% filter(control==1, marketing==0))$balchange
+x = list(control_balchange, marketing_balchange, seed_balchange)
+pJCK(x, method="Monte Carlo")
+
+```
+
 ### 4.3 Discussion of Results
+
+A p-value of 0.0001 means that we reject the null hypothesis in favor of the alternate.
 

### 2020-07-26 draft.Rmd
Add Tukey HSD as well as Fligner-Policello

@@
 seed_accounts = treated %>% filter(treatment == 1)
+nonseed = treated %>% filter(treatment == 0)
 hist(seed_accounts$balchange,
@@
 summary(seed_accounts$balchange)
+
+filtered_nonseeds = nonseed %>% filter(balchange<10000)
+hist(nonseed$balchange)
+hist(filtered_nonseeds$balchange)
+
 ```
@@
 
+We know very little about the difference in the underlying distributions of the SEED account savings and the non SEED account savings.
+We can reasonably assuming independence from each other and continuity of both distributions, but not much else.
+However, the closest test that matches those assumptions is the Fligner-Policello Test.
+
+The Fligner-Policello Test tests for a difference in population median, but it requires both populations to be symmetric.
+We feel comfortable violating this assumption here for two reasons.
+One is that once the comparably small number of outliers are removed, the distributions start to become symmetric.
+The second reason is that this is the most permissive test of center available to us.
+
+We will run this test at a significance level of $\alpha=0.05$ with the following hypothesis.
+
+$H_0: \theta_x = \theta_y$
+
+$H_a: \theta_x < \theta_y$
+
+Where $\theta_x$ represents the true median of the difference in balance changes for the control group and $\theta_y$ represents the true median of the difference in balance changes for SEED accounts.
+
+In addition to testing whether or not the SEED accounts are more effective savings than a control group, we also want to confirm that the SEED accounts are more effective than just the marketing that comes with them.
+To do this we divide the customers into three groups.
+A control group, a group that receives marketing but not SEED accounts, and the group with SEED accounts.
+
+Since we have reason to believe that marketing about savings will be more effective than no marketing, and that marketing plus a SEED account will be more effective than just marketing, we will use an ordered k-sample test.
+Here we use the Jonckheere-Terpstra test as recommended by Higgins.
+[@Higgins]
+
+We will conduct this test at a significance level of $\alpha=0.05$ with the following hypothesis.
+
+$H_0: \theta_x = \theta_y = \theta_z$
+
+$H_a: \theta_x \leq \theta_y \leq \theta_z$ with at least one strict inequality
+
+Where $\theta_x, \theta_y, \theta_z$ are the medians of the distributions of the savings in the control group, the marketing group, and the SEED accounts respectively.
+
 ### 4.2 Results
+
+```{r 2-sample}
+x = list(nonseed$balchange, seed_accounts$balchange)
+pFligPoli(x, method="Monte Carlo")
+```
 
@@
 pJCK(x, method="Monte Carlo")
+```
 
+```{r Tukey HSD setup}
+# Helper functions
+comp_sum = function(val, t1){
+# Helper function for Mann-Whitney stat
+  full = sum(t1 < val)
+  partial = 0.5 * sum(t1 == val)
+  return(full+partial)
+}
+
+mw_stat = function(t1, t2){
+  #Mann-Whitney statistic for two treatments
+  comp_sums = mapply(comp_sum, t2, MoreArgs = list(t1=t1))
+  return(sum(comp_sums))
+}
+
+general_stat_perm= function(full_data, n_s, stat_func){
+  # stat_func should take in a list of 
+  dataset = list()
+  k = length(n_s)
+  start=1
+  end=0
+  for (i in 1:k){
+    end = end + n_s[i]
+    dataset[[i]] = full_data[start:end]
+    start = end + 1
+  }
+  return(stat_func(dataset))
+}
+
+calculate_critical = function(stat_dist, alpha){
+  # stat_dist is sorted
+  R = length(stat_dist)
+  init_crit = stat_dist[R*alpha]
+  if(sum(sample_q >= init_crit)/R == alpha){
+    return(init_crit)
+  }
+  index = sum(sample_q > init_crit)
+  return(sample_q[index])
+}
+
+```
+
+```{r Tukey HSD}
+
+# Permutation Tukey HSD test
+q_star = function(dataset){
+  # Permutation HSD pg 97
+  # Use the Mann-Whitney for T
+  k = length(dataset)
+  max_t = 0
+  for (i in 1:(k-1)) {
+    for(j in (i+1):k){
+      t = abs(mw_stat(dataset[[i]], dataset[[j]]))
+      if (t > max_t){
+        max_t = t
+      }
+    }
+  }
+  return(max_t)
+}
+
+treat_list = list(
+  control=control_balchange,
+  marketing=marketing_balchange,
+  seed=seed_balchange
+)
+
+k = length(treat_list)
+n_s = mapply(length, treat_list)
+N = sum(n_s)
+full_data = unlist(treat_list)
+
+R = 10000
+permutations = matrix(NA, ncol = N, nrow=R)
+for (i in 1:R){
+  permutations[i,] = sample(full_data)
+}
+sample_q = apply(permutations, 1, general_stat_perm, n_s, q_star)
+sample_q = sort(sample_q, decreasing = TRUE)
+
+a_1 = calculate_critical(sample_q, 0.1)
+a_05 = calculate_critical(sample_q, 0.05)
+crit_message = sprintf("critical values of significance levels 0.1 and 0.05 are %s and %s respectively", a_1, a_05)
+print(crit_message)
+
+q_obs = q_star(treat_list)
+obs_message = sprintf("The observed value of Q* is: %s", q_obs)
+print(obs_message)
+
+counts = sum(sample_q>= q_obs)
+p_val = counts/R
+p_message = sprintf("With a p-value of %s", p_val)
+print(p_message)
+
+```
+
+```{r}
+m = matrix(NA, k, k, 
+           dimnames = list(
+             names(treat_list),
+             names(treat_list)
+            )
+          )
+
+for (row in names(treat_list)){
+  for(col in names(treat_list)){
+    m[row,col] = mw_stat(treat_list[[row]], treat_list[[col]])
+  }
+}
+print("pairwise statistics greater than or equal to the 0.05 critical value")
+print(m >= a_05)
 ```
@@
 
-A p-value of 0.0001 means that we reject the null hypothesis in favor of the alternate.
+A p-value of 0.0001 for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternate.
+We conclude that the median savings for SEED accounts is higher an for non-SEED accounts.
+
+A p-value of 0.0001 for the Jonckheere-Terpstra test means that we reject the null hypothesis in favor of the alternate. We conclude that there is a difference in savings between the three groups.
+
+A p-value of 0 for the Tukey HSD permutation test shows that the SEED account is awesome.
+The matrix shows that the SEED accounts had better savings than the control group and the marketing groups.
+No other differences were significant.
 

### 2020-07-26 draft.Rmd
Add draft introduction and begin describing the data

--- 2020-07-26 draft.Rmd
@@
 ```{r load-data}
-seed011204 = read_stata("dataverse_files/seedanalysis_011204.dta")
+seed011204 =read_stata("dataverse_files/seedanalysis_011204.dta")
 
@@
 
+### Luke Botti and Aaron R. Williams
+
 ## 1. Introduction
+
+Personal savings can be a financial buffer during emergencies and economic downturns, are an important catalyst to large purchases like appliances and investments in housing and education, and are essential to maintaining consumption in retirement.
+Accordingly, promoting and increasing personal savings is an important policy goal for governments, employers, and communities.
+
+One possible intervention is a commitment savings account, which when opened is a savings account that restricts the account holder's access to the balance until a savings goal is achieved, a fixed period of time has passed, or an emergency occurs.
+The accounts have no other benefits like bonuses or preferred interest rates.
+
+[@Ashraf2006] implemented a randomized control trial (RCT) to 1.
+see if individuals offered the account open the accounts, and if so, what characteristics are associated with opening an account and 2.
+if individuals save more as a result of opening the account.
+
+The authors find that individuals open the accounts when offered.
+They also find that women are statistically significantly more likely to open accounts if they have hyperbolic preferences.
+They did not find a significant result for men.
+People have hyperbolic preferences if they exhibit a high discount rate in the immediate future and a lower discount rate further in the future.
+Accordingly, these individuals can improve their welfare with a commitment savings device.
+
+The authors find that average savings increased by 81 percent for those in the treatment group relative to the control group after twelve months.
+The effect is significant at the $\alpha = 0.1$ level; however, the outcome variable is highly positively skewed.
+
+We conduct a reanalysis using data shared by the authors using nonparametric methods.
+Parametric statistical methods, such as many of the methods used by the authors, require completely specifying the form of the population distribution of interest except for a finite number of parameters [@Higgins].
+In contrast, nonparametric statistical methods require minimal assumptions about the population distribution.
+In this case, nonparametric methods will be more robust to skew in the outcome variable of interest.
+
+We find... todo(aaron): add a paragraph summarizing our conclusions
 
@@
 
-```{r}
-seed_accounts = treated %>% filter(treatment == 1)
-hist(seed_accounts$balchange,
-     main="Histogram of balance changes for SEED accounts",
-     xlab="Balance Change")
+The data and code for [@Ashraf2006] are available on the Harvard Dataverse [@Data].
+The repository contains Stata `.do` files for all models and tables included in the authors' paper.
+The repository contains three data sets.
 
-filtered_seeds = seed_accounts %>% filter(balchange <=10000)
-hist(filtered_seeds$balchange,
-     main="Outliers removed balance changes for SEED accounts",
-     xlab="Balance Change")
+The first contains information after six months.
+The second contains information after twelve months.
+The third data set contains information about the change in balances after six months and twelve months.
+The authors did not include documentation for the numerous variables included in the data set.
+We recreated Table II, Table VI, and Table VII in `R` to back out the variable definitions and confirm that the published table matches the published table.
 
-print("Summary statistics for Seed account balance changes")
-summary(seed_accounts$balchange)
-```
+todo(aaron): include a brief visual summary of the data
+
+Number of observations
 
@@
 
-We will use a one sided Wilcoxon Signed-Rank Test at a significance of $\alpha=0.05$ to test if the the savings of customers with SEED accounts increased.
-
-We will be testing the following hypothesis where $\theta_d$ is the mean of the differences in savings for customers with SEED accounts from before and after the trial
-
-$H_0: \theta_d = 0$
-
-$H_a: \theta_d >0$
-
-We will be used a Signed-Rank test given the significant outliers in the data.
-
-The Wilcoxon Signed-Rank Test statistic is done by ranking the absolute values of the paired differences.
-The ranks are then signed positive or negative based on whether or not the corresponding differences are positive or negative.
-The test statistic is the sum of the positive ranks.
-As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with
-$E(SR_+) = \frac{n(n+1)}{4} = `r (842 * (842 + 1)) / 4`$ and 
-$\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=`r (842 * (842 + 1) * (2 * 842 + 1) / 24)`$. [@Higgins]
-
 ### 3.2 Results
 
-```{r}
-wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)
-
-```
-
 ### 3.3 Discussion of Results
-
-As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternate hypothesis.
-We conclude that customers who had SEED accounts saw an increase in savings over the duration of the trial.
-It is worth noting that we have not yet shown that the SEED accounts are more effective savings accounts than other methods, just that customers were able to save with them.
 
@@
 ## 5. Robust Regression
+
+log; however, non-positive values
 

### 2020-07-26 draft.Rmd

@@
 ```{r load-data}
-seed011204 =read_stata("dataverse_files/seedanalysis_011204.dta")
+seed011204 = read_stata("dataverse_files/seedanalysis_011204.dta")
 
@@
 
+```{r}
+seed_accounts = treated %>% filter(treatment == 1)
+hist(seed_accounts$balchange,
+     main="Histogram of balance changes for SEED accounts",
+     xlab="Balance Change")
+
+filtered_seeds = seed_accounts %>% filter(balchange <=10000)
+hist(filtered_seeds$balchange,
+     main="Outliers removed balance changes for SEED accounts",
+     xlab="Balance Change")
+
+print("Summary statistics for Seed account balance changes")
+summary(seed_accounts$balchange)
+```
+
 ## 3. Paired Comparisons
@@
 
+We will use a one sided Wilcoxon Signed-Rank Test at a significance of $\alpha=0.05$ to test if the the savings of customers with SEED accounts increased.
+
+We will be testing the following hypothesis where $\theta_d$ is the mean of the differences in savings for customers with SEED accounts from before and after the trial
+
+$H_0: \theta_d = 0$
+
+$H_a: \theta_d >0$
+
+We will be used a Signed-Rank test given the significant outliers in the data.
+
+The Wilcoxon Signed-Rank Test statistic is done by ranking the absolute values of the paired differences.
+The ranks are then signed positive or negative based on whether or not the corresponding differences are positive or negative.
+The test statistic is the sum of the positive ranks.
+As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with
+$E(SR_+) = \frac{n(n+1)}{4} = `r (842 * (842 + 1)) / 4`$ and 
+$\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=`r (842 * (842 + 1) * (2 * 842 + 1) / 24)`$. [@Higgins]
+
 ### 3.2 Results
 
+```{r}
+wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)
+
+```
+
 ### 3.3 Discussion of Results
+
+As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternate hypothesis.
+We conclude that customers who had SEED accounts saw an increase in savings over the duration of the trial.
+It is worth noting that we have not yet shown that the SEED accounts are more effective savings accounts than other methods, just that customers were able to save with them.
 

### 2020-07-27 draft.Rmd
remove JT test, flesh out Tukey Perm HSD

--- 2020-07-26 draft.Rmd
@@
 
-```{r}
+```{r wilcox paired test}
 wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)
-
 ```
@@
 
-Since we have reason to believe that marketing about savings will be more effective than no marketing, and that marketing plus a SEED account will be more effective than just marketing, we will use an ordered k-sample test.
-Here we use the Jonckheere-Terpstra test as recommended by Higgins.
-[@Higgins]
+We will use the Tukey Permutation HSD Test to conduct a multiple comparison test of these groups.
+The test statistic will be calculated by taking the maximum absolute value of the Mann-Whitney statistic for each pairwise comparison of the three groups.
+The p-value will be calculated with a re-sampling approach.
+We will shuffle the data between groups and recalculate the test statistic 10,000 times.
+The estimated p-value will be the percentage of test statistics greater than or equal to the observed.
 
@@
 
-$H_a: \theta_x \leq \theta_y \leq \theta_z$ with at least one strict inequality
+$H_a$
+
+To control for type one error we will use Bonferroni's adjustment for the paired test. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (k * (k - 1))`$[@Higgins]
 
@@
 pFligPoli(x, method="Monte Carlo")
-```
-
-```{r k-sample JT test}
-
-seed_balchange = seed_accounts$balchange
-marketing_balchange = (treated %>% filter(marketing==1))$balchange
-control_balchange = (treated %>% filter(control==1, marketing==0))$balchange
-x = list(control_balchange, marketing_balchange, seed_balchange)
-pJCK(x, method="Monte Carlo")
 ```
@@
 
+seed_balchange = seed_accounts$balchange
+marketing_balchange = (treated %>% filter(marketing==1))$balchange
+control_balchange = (treated %>% filter(control==1, marketing==0))$balchange
+
 # Permutation Tukey HSD test
@@
 
-a_1 = calculate_critical(sample_q, 0.1)
-a_05 = calculate_critical(sample_q, 0.05)
-crit_message = sprintf("critical values of significance levels 0.1 and 0.05 are %s and %s respectively", a_1, a_05)
+alpha = 0.05
+adjusted_alpha = 2*alpha/ (k*(k-1))
+print(sprintf("Alpha of %s leads to an adjusted alpha of %s", alpha, adjusted_alpha))
+
+crit_alpha = calculate_critical(sample_q, alpha)
+crit_adj = calculate_critical(sample_q, adjusted_alpha)
+crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
 print(crit_message)
@@
 }
-print("pairwise statistics greater than or equal to the 0.05 critical value")
-print(m >= a_05)
+print("pairwise statistics greater than or equal to the adjusted alpha critical value")
+print(m >= crit_adj)
 ```
@@
 
-A p-value of 0.0001 for the Jonckheere-Terpstra test means that we reject the null hypothesis in favor of the alternate. We conclude that there is a difference in savings between the three groups.
+A p-value of 0 for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative.
+We conclude that there is a difference in savings between at least two of the groups.
 
-A p-value of 0 for the Tukey HSD permutation test shows that the SEED account is awesome.
 The matrix shows that the SEED accounts had better savings than the control group and the marketing groups.
 No other differences were significant.
+This allows us to conclude that the SEED accounts had better savings than the other two groups.
 

### 2020-07-27 draft.Rmd
fix inline R calc
Add transformation language, describe the RCT, and add sample size information

--- 2020-07-26 draft.Rmd
@@
 
+The authors partnered with a rural bank in Mindanao, Philippines called Green Bank of Caraga.
+After two rounds of randomization, they ended up with a survey size of 1,777 people who completed a baseline household survey.
+They then randomly assigned the individuals to the commitment treatment (T), marketing-treatment (M), and control (C) groups.
+One concern is that the commitment-savings may have a treatment effect because of the outreach or positive messaging around savings.
+The marketing treatment (M), a special visit to encourage savings using existing savings products only, was included to evaluate this effect.
+The marketing-treatment can also be thought of as a control.
+There were no pre-treatment significant differences between the three groups for observable characteristics.
+
+The two main outcomes of interest are 1.
+take-up of the commitment savings product and 2.
+savings at the financial institution.
+The authors use the baseline household survey to evaluate if there are any predictors to take-up.
+Savings balances at the institution, and not just in the commitment savings account, partially accounts for crowd-out to other savings vehicles.
+
 The authors find that individuals open the accounts when offered.
@@
 The effect is significant at the $\alpha = 0.1$ level; however, the outcome variable is highly positively skewed.
+
+todo(aaron): address quantile regression
 
@@
 
-The data and code for [@Ashraf2006] are available on the Harvard Dataverse [@Data].
-The repository contains Stata `.do` files for all models and tables included in the authors' paper.
+The data and code for [@Ashraf2006] are available on the Harvard Dataverse [@Data]. The repository contains Stata `.do` files for all models and tables included in the authors' paper.
+
 The repository contains three data sets.
-
-The first contains information after six months.
-The second contains information after twelve months.
+All three data sets include identifiers and certain demographic information.
+The first data set contains outcome information after six months.
+The second data set contains outcome information after twelve months.
 The third data set contains information about the change in balances after six months and twelve months.
@@
 
-todo(aaron): include a brief visual summary of the data
+The authors began with a sample of 4,001 clients who have savings accounts in of two bank branches in the greater Butuan City area and have identifiable addresses.
+A second randomization resulted in 3,154 potential surveys and 1,777 completed surveys.
 
-Number of observations
+```{r}
+#
+# Create a plot to show the skew of balchange
+#
+skewa = six_months %>%
+  ggplot(aes(balchange)) +
+  geom_density() +
+  scale_x_continuous(labels = scales::comma) +
+  scale_y_continuous(limits = c(0, 0.004)) +
+  labs(title = "The Dependent Variables Are Highly Right Skewed",
+       subtitle = "Six Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",       
+       y = NULL) +
+  theme_minimal()
+
+skewb = treated %>%
+  ggplot(aes(balchange)) +
+  geom_density() +
+  scale_x_continuous(labels = scales::comma) +
+  scale_y_continuous(limits = c(0, 0.004)) +
+  labs(title = "",
+       subtitle = "Twelve Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal()
+
+skewa + skewb
+
+rm(skewa, skewb)
+
+```
+
+```{r}
+#
+# Create a plot to show the skew of balchange by group
+#
+skewa = six_months %>%
+  ggplot(aes(balchange, y = group, color = group)) +
+  geom_point(alpha = 0.2) +
+  scale_x_continuous(labels = scales::comma) +
+  labs(title = "The Dependent Variables Are Highly Right Skewed",
+       subtitle = "Six Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",       
+       y = NULL) +
+  theme_minimal() +
+  guides(color = FALSE)
+
+skewb = treated %>%
+  ggplot(aes(balchange, y = group, color = group)) +
+  geom_point(alpha = 0.2) +
+  scale_x_continuous(labels = scales::comma) +
+  labs(title = "",
+       subtitle = "Twelve Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal() +
+  guides(color = FALSE)
+
+skewa + skewb
+
+rm(skewa, skewb)
+
+```
 
@@
 
-log; however, non-positive values
-
 [@Ashraf2006] estimate regression models with change in savings account balance as the dependent variable and the different treatments and controls as independent variables.
@@
 
-The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months.
+The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months as demonstrated in [todo(aaron): add plot number from above].
 Accordingly, the dependent variable is not approximately normally distributed and the error term of their estimated models is not approximately normally distributed.
 
-```{r}
-#
-# Create a plot to show the skew of balchange
-#
-skewa = six_months %>%
-  ggplot(aes(balchange)) +
-  geom_density() +
-  scale_x_continuous(labels = scales::comma) +
-  scale_y_continuous(limits = c(0, 0.004)) +
-  labs(title = "The Dependent Variables Are Highly Right Skewed",
-       subtitle = "Six Month Change in Balance",
-       x = "Change in balance (Philippine Peso)",       
-       y = NULL) +
-  theme_minimal()
+[todo(aaron): add plot number from above] The SEED treatment, the marketing control, and the full control all have outliers.
+Though the SEED treatment's outliers are distinct for the change in twelve month balance.
 
-skewb = treated %>%
-  ggplot(aes(balchange)) +
-  geom_density() +
-  scale_x_continuous(labels = scales::comma) +
-  scale_y_continuous(limits = c(0, 0.004)) +
-  labs(title = "",
-       subtitle = "Twelve Month Change in Balance",
-       x = "Change in balance (Philippine Peso)",
-       y = NULL) +  
-  theme_minimal()
+A normal distribution and ordinary least squares regression do not seem appropriate in this situation.
+One option is to transform the outcome variable before estimation so that normal-theory methods can be applied to the data.
+A log transformation would be appropriate but the presence of non-positive numbers would lead to an undefined outcome.
+An inverse hyperbolic sine transformation [@Burbidge] or Yeo-Johnson transformation [@Yeo] could result in a similar transformation to a log transformation and be robust to non-positive numbers.
 
-skewa + skewb
-
-rm(skewa, skewb)
-
-```
-
-The SEED treatment, the marketing control, and the full control all have outliers. Though the SEED treatment's outliers are distinct for the change in twelve month balance.
-
-```{r}
-#
-# Create a plot to show the skew of balchange by group
-#
-skewa = six_months %>%
-  ggplot(aes(balchange, y = group, color = group)) +
-  geom_point(alpha = 0.2) +
-  scale_x_continuous(labels = scales::comma) +
-  labs(title = "The Dependent Variables Are Highly Right Skewed",
-       subtitle = "Six Month Change in Balance",
-       x = "Change in balance (Philippine Peso)",       
-       y = NULL) +
-  theme_minimal() +
-  guides(color = FALSE)
-
-skewb = treated %>%
-  ggplot(aes(balchange, y = group, color = group)) +
-  geom_point(alpha = 0.2) +
-  scale_x_continuous(labels = scales::comma) +
-  labs(title = "",
-       subtitle = "Twelve Month Change in Balance",
-       x = "Change in balance (Philippine Peso)",
-       y = NULL) +  
-  theme_minimal() +
-  guides(color = FALSE)
-
-skewa + skewb
-
-rm(skewa, skewb)
-
-# measure of outliers from 611?
-
-```
-
-[@Ashraf2006] found only modest evidence for a statistically significant intent-to-treat (ITT) effect for the commitment savings accounts using ordinary least squares regression (OLS).
+[@Ashraf2006] estimate their models on the untransformed data and find only modest evidence for a statistically significant intent-to-treat (ITT) effect for the commitment savings accounts using ordinary least squares regression (OLS).
 Furthermore, they found that the differential effect of being offered the commitment savings product beyond being offered only a marketing treatment was indistinguishable from zero.
@@
 #
-six_months = filter(seed011204, !is.na(treatment))
 
@@
 ### 5.3 Discussion of Results
+
+1. plot residuals
+2. measures of outliers
 

### 2020-07-27 draft.Rmd
addressed some PR comments

--- 2020-07-27 draft.Rmd
@@
 ```{r}
-seed_accounts = treated %>% filter(treatment == 1)
-nonseed = treated %>% filter(treatment == 0)
+seed_accounts = treated %>% 
+  filter(treatment == 1)
+nonseed = treated %>% 
+  filter(treatment == 0)
 hist(seed_accounts$balchange,
@@
 
-We will be testing the following hypothesis where $\theta_d$ is the mean of the differences in savings for customers with SEED accounts from before and after the trial
+We will be testing the following hypothesis where $\theta_d$ is the median of the differences in savings for customers with SEED accounts from before and after the trial
 
@@
 $\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=`r (842 * (842 + 1) * (2 * 842 + 1) / 24)`$. [@Higgins]
+
+The Wilcoxon Signed-Rank Test requires three assumptions:
+
+1. The data is paired and comes from the same population
+2. Each pair is chosen randomly and independently
+3. The data is continuous.
 
@@
 
-$H_a$
+$H_a: \exists i,j \text{ s.t. } \theta_i \leq\theta_j$ and $i,j\in \{x,y,z\}$
 
-To control for type one error we will use Bonferroni's adjustment for the paired test. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (k * (k - 1))`$[@Higgins]
+To control for type one error we will use Bonferroni's adjustment for the paired test. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins]
 
@@
 seed_balchange = seed_accounts$balchange
-marketing_balchange = (treated %>% filter(marketing==1))$balchange
-control_balchange = (treated %>% filter(control==1, marketing==0))$balchange
+marketing_balchange = treated %>% 
+  filter(marketing==1)%>%
+  pull(balchange)
+control_balchange = treated %>% 
+  filter(control==1, marketing==0) %>%
+  pull(balchange)
 

### 2020-07-27 draft.Rmd
dynamic p-values

@@
 x = list(nonseed$balchange, seed_accounts$balchange)
-pFligPoli(x, method="Monte Carlo")
+fp_result = pFligPoli(x, method="Monte Carlo")
+fp_result
 ```
@@
 
-A p-value of 0.0001 for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternate.
+A p-value of `r fp_result$p.val` for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternate.
 We conclude that the median savings for SEED accounts is higher an for non-SEED accounts.
 
-A p-value of 0 for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative.
+A p-value of `r p_val` for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative.
 We conclude that there is a difference in savings between at least two of the groups.

### 2020-07-28 draft.Rmd
Add paragraph about quantile regression

--- 2020-07-27 draft.Rmd
@@
 
-todo(aaron): address quantile regression
+The authors also estimate quantile regressions at the 10th through 90th deciles.
+The estimated effects are significant after 12 months when comparing the commitment-saving group with the full control group.
+The statistical and practical significance disappears when comparing the commitment-savings group with the marketing group.
 

### 2020-07-28 draft.Rmd
Fix tense

@@
 [@Ashraf2006] implemented a randomized control trial (RCT) to 1.
-see if individuals offered the account open the accounts, and if so, what characteristics are associated with opening an account and 2.
-if individuals save more as a result of opening the account.
+see if individuals offered accounts opens accounts, and if so, what characteristics are associated with opening an account and 2.
+if individuals save more as a result of opening an account.
 
@@
 The marketing-treatment can also be thought of as a control.
-There were no pre-treatment significant differences between the three groups for observable characteristics.
+No pre-treatment observable differences between the three groups were statistically significantly different.
 
@@
 The authors also estimate quantile regressions at the 10th through 90th deciles.
-The estimated effects are significant after 12 months when comparing the commitment-saving group with the full control group.
+The estimated effects are significant after 12 months when comparing the commitment-savings group with the full control group.
 The statistical and practical significance disappears when comparing the commitment-savings group with the marketing group.
@@
 The authors did not include documentation for the numerous variables included in the data set.
-We recreated Table II, Table VI, and Table VII in `R` to back out the variable definitions and confirm that the published table matches the published table.
+We recreated Table II, Table VI, and Table VII in `R` to back out the variable definitions and confirm that the published data match the published tables.
 
-The authors began with a sample of 4,001 clients who have savings accounts in of two bank branches in the greater Butuan City area and have identifiable addresses.
+The authors began with a sample of 4,001 clients who have savings accounts in one of two bank branches in the greater Butuan City area and have identifiable addresses.
 A second randomization resulted in 3,154 potential surveys and 1,777 completed surveys.
+
+The key outcomes of interest for this reanalysis, the change in balance after six months and the change in balance after twelve months, are both highly right skewed.
 
@@
 ```
+
+The right skew is present in the treatment and control groups, but it most pronounced in the commit-savings treatment group after twelve months.
 

### 2020-07-28 draft.Rmd

--- 2020-07-27 draft.Rmd
@@
 
+### Luke Botti and Aaron R. Williams
+
 ## 1. Introduction
 
+Personal savings can be a financial buffer during emergencies and economic downturns, are an important catalyst to large purchases like appliances and investments in housing and education, and are essential to maintaining consumption in retirement.
+Accordingly, promoting and increasing personal savings is an important policy goal for governments, employers, and communities.
+
+One possible intervention is a commitment savings account, which when opened is a savings account that restricts the account holder's access to the balance until a savings goal is achieved, a fixed period of time has passed, or an emergency occurs.
+The accounts have no other benefits like bonuses or preferred interest rates.
+
+[@Ashraf2006] implemented a randomized control trial (RCT) to 1.
+see if individuals offered accounts opens accounts, and if so, what characteristics are associated with opening an account and 2.
+if individuals save more as a result of opening an account.
+
+The authors partnered with a rural bank in Mindanao, Philippines called Green Bank of Caraga.
+After two rounds of randomization, they ended up with a survey size of 1,777 people who completed a baseline household survey.
+They then randomly assigned the individuals to the commitment treatment (T), marketing-treatment (M), and control (C) groups.
+One concern is that the commitment-savings may have a treatment effect because of the outreach or positive messaging around savings.
+The marketing treatment (M), a special visit to encourage savings using existing savings products only, was included to evaluate this effect.
+The marketing-treatment can also be thought of as a control.
+No pre-treatment observable differences between the three groups were statistically significantly different.
+
+The two main outcomes of interest are 1.
+take-up of the commitment savings product and 2.
+savings at the financial institution.
+The authors use the baseline household survey to evaluate if there are any predictors to take-up.
+Savings balances at the institution, and not just in the commitment savings account, partially accounts for crowd-out to other savings vehicles.
+
+The authors find that individuals open the accounts when offered.
+They also find that women are statistically significantly more likely to open accounts if they have hyperbolic preferences.
+They did not find a significant result for men.
+People have hyperbolic preferences if they exhibit a high discount rate in the immediate future and a lower discount rate further in the future.
+Accordingly, these individuals can improve their welfare with a commitment savings device.
+
+The authors find that average savings increased by 81 percent for those in the treatment group relative to the control group after twelve months.
+The effect is significant at the $\alpha = 0.1$ level; however, the outcome variable is highly positively skewed.
+
+The authors also estimate quantile regressions at the 10th through 90th deciles.
+The estimated effects are significant after 12 months when comparing the commitment-savings group with the full control group.
+The statistical and practical significance disappears when comparing the commitment-savings group with the marketing group.
+
+We conduct a reanalysis using data shared by the authors using nonparametric methods.
+Parametric statistical methods, such as many of the methods used by the authors, require completely specifying the form of the population distribution of interest except for a finite number of parameters [@Higgins].
+In contrast, nonparametric statistical methods require minimal assumptions about the population distribution.
+In this case, nonparametric methods will be more robust to skew in the outcome variable of interest.
+
+We find... todo(aaron): add a paragraph summarizing our conclusions
+
 ## 2. Summary of Data for Analysis
+
+The data and code for [@Ashraf2006] are available on the Harvard Dataverse [@Data]. The repository contains Stata `.do` files for all models and tables included in the authors' paper.
+
+The repository contains three data sets.
+All three data sets include identifiers and certain demographic information.
+The first data set contains outcome information after six months.
+The second data set contains outcome information after twelve months.
+The third data set contains information about the change in balances after six months and twelve months.
+The authors did not include documentation for the numerous variables included in the data set.
+We recreated Table II, Table VI, and Table VII in `R` to back out the variable definitions and confirm that the published data match the published tables.
+
+The authors began with a sample of 4,001 clients who have savings accounts in one of two bank branches in the greater Butuan City area and have identifiable addresses.
+A second randomization resulted in 3,154 potential surveys and 1,777 completed surveys.
+
+The key outcomes of interest for this reanalysis, the change in balance after six months and the change in balance after twelve months, are both highly right skewed.
+
+```{r}
+#
+# Create a plot to show the skew of balchange
+#
+skewa = six_months %>%
+  ggplot(aes(balchange)) +
+  geom_density() +
+  scale_x_continuous(labels = scales::comma) +
+  scale_y_continuous(limits = c(0, 0.004)) +
+  labs(title = "The Dependent Variables Are Highly Right Skewed",
+       subtitle = "Six Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",       
+       y = NULL) +
+  theme_minimal()
+
+skewb = treated %>%
+  ggplot(aes(balchange)) +
+  geom_density() +
+  scale_x_continuous(labels = scales::comma) +
+  scale_y_continuous(limits = c(0, 0.004)) +
+  labs(title = "",
+       subtitle = "Twelve Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal()
+
+skewa + skewb
+
+rm(skewa, skewb)
+
+```
+
+The right skew is present in the treatment and control groups, but it most pronounced in the commit-savings treatment group after twelve months.
+
+```{r}
+#
+# Create a plot to show the skew of balchange by group
+#
+skewa = six_months %>%
+  ggplot(aes(balchange, y = group, color = group)) +
+  geom_point(alpha = 0.2) +
+  scale_x_continuous(labels = scales::comma) +
+  labs(title = "The Dependent Variables Are Highly Right Skewed",
+       subtitle = "Six Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",       
+       y = NULL) +
+  theme_minimal() +
+  guides(color = FALSE)
+
+skewb = treated %>%
+  ggplot(aes(balchange, y = group, color = group)) +
+  geom_point(alpha = 0.2) +
+  scale_x_continuous(labels = scales::comma) +
+  labs(title = "",
+       subtitle = "Twelve Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal() +
+  guides(color = FALSE)
+
+skewa + skewb
+
+rm(skewa, skewb)
+
+```
 
@@
      xlab="Balance Change")
-
 filtered_seeds = seed_accounts %>% filter(balchange <=10000)
@@
      xlab="Balance Change")
-
 print("Summary statistics for Seed account balance changes")
 summary(seed_accounts$balchange)
-
 filtered_nonseeds = nonseed %>% filter(balchange<10000)
@@
 hist(filtered_nonseeds$balchange)
-
 ```
@@
 
-M-estimation and robust rank-based regression lead to very different results than ordinary least squares.
+The models estimated with OLS have residuals that are highly skewed.
+The following QQ plots demonstrate that many of the residuals are approximately normally distributed, as they fall on the diagonal line.
+However, the residuals dramatically depart the line at higher values.
+
+```{r}
+resid1 = augment(lm3) %>%
+  ggplot(aes(sample = .resid)) +
+  geom_qq(alpha = 0.2) +
+  geom_qq_line() +
+  theme_minimal() +
+  labs(title = "The Estimated Model has Significant Outliers",
+       subtitle = "QQ Plot for OLS (3)")
+
+resid2 = augment(lm3) %>%
+  ggplot(aes(sample = .resid)) +
+  geom_qq(alpha = 0.2) +
+  geom_qq_line() +
+  theme_minimal() +
+  labs(title = "",
+       subtitle = "QQ Plot for OLS (4)")
+
+resid1 + resid2
+
+```
+
+Accordingly, M-estimation and robust rank-based regression lead to very different results than ordinary least squares.
 

### 2020-07-28 draft.Rmd
Address Luke's feedback for sections 1 and 2

@@
 Savings balances at the institution, and not just in the commitment savings account, partially accounts for crowd-out to other savings vehicles.
+We focus exclusively on question 2.
 
-The authors find that individuals open the accounts when offered.
+For the first question, the authors find that individuals open the accounts when offered.
 They also find that women are statistically significantly more likely to open accounts if they have hyperbolic preferences.
@@
 Accordingly, these individuals can improve their welfare with a commitment savings device.
+We do not examine these results.
 
-The authors find that average savings increased by 81 percent for those in the treatment group relative to the control group after twelve months.
+For the second question, the authors find that average savings increased by 81 percent for those in the treatment group relative to the control group after twelve months.
 The effect is significant at the $\alpha = 0.1$ level; however, the outcome variable is highly positively skewed.
@@
 
-We find... todo(aaron): add a paragraph summarizing our conclusions
+We conclude using paired comparisons that customers who had SEED accounts saw an increase in savings over the duration of the trial.
+We conclude using Tukey Permutation Honest Significant Difference tests that SEED accounts had more savings than the other two groups.
+Finally, using M-Estimation and rank-based and robust regression we find that SEED accounts had more savings than the other two groups; however, we find much smaller effect sizes than [@Ashraf2006].
+
+Section 2 describes and summarizes the analysis data.
+In section 3, we test the effectiveness of the SEED accounts on overall savings.
+In section 4, we test the effectiveness of the SEED accounts against the control group and the marketing treatment.
+In section 5, use use robust regression techniques to estimate linear regression models that are more appropriate in the presence of outliers.
 
@@
 #
-# Create a plot to show the skew of balchange
+# Create a histogram to show the skew of balchange
+#
+skewa = six_months %>%
+  ggplot(aes(balchange)) +
+  geom_histogram() +
+  scale_x_continuous(labels = scales::comma) +
+  scale_y_continuous(limits = c(0, 2000),
+                     labels = scales::comma) +
+  labs(title = "The Dependent Variables Are Highly Right Skewed",
+       subtitle = "Six Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",       
+       y = NULL) +
+  theme_minimal()
+
+skewb = treated %>%
+  ggplot(aes(balchange)) +
+  geom_histogram() +
+  scale_x_continuous(labels = scales::comma) +
+  scale_y_continuous(limits = c(0, 2000),
+                     labels = scales::comma) +
+  labs(title = "",
+       subtitle = "Twelve Month Change in Balance",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal()
+
+skewa + skewb
+
+rm(skewa, skewb)
+
+```
+
+Here is the same information as a kernel density estimate (KDE).
+
+```{r}
+#
+# Create a density plot to show the skew of balchange
 #
@@
   filter(treatment == 0)
-hist(seed_accounts$balchange,
-     main="Histogram of balance changes for SEED accounts",
-     xlab="Balance Change")
-filtered_seeds = seed_accounts %>% filter(balchange <=10000)
-hist(filtered_seeds$balchange,
-     main="Outliers removed balance changes for SEED accounts",
-     xlab="Balance Change")
-print("Summary statistics for Seed account balance changes")
-summary(seed_accounts$balchange)
-filtered_nonseeds = nonseed %>% filter(balchange<10000)
-hist(nonseed$balchange)
-hist(filtered_nonseeds$balchange)
+
 ```

### 2020-07-28 draft.Rmd

@@
 
-```{r}
+```{r histogram}
 #
@@
 
-```{r}
+```{r density-plot}
 #
@@
 
-```{r}
+```{r skew-by-group}
 #
@@
 
-```{r}
+```{r subset-data}
 seed_accounts = treated %>% 
@@
 
-```{r wilcox paired test}
+```{r wilcox-paired-test}
 wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)
+
 ```
@@
 
-```{r Tukey HSD setup}
+```{r Tukey-HSD-setup}
 # Helper functions
@@
 
-```{r Tukey HSD}
+```{r Tukey-HSD}
 
@@
 
-```{r}
+```{r pairwise-results}
 m = matrix(NA, k, k, 
@@
 print(m >= crit_adj)
+
 ```
@@
 
-```{r}
+```{r balchange-direction}
 #
@@
 
-```{r}
+```{r blachange-direction-by-group}
 count(treated, group, change) %>%
@@
 
-```{r}
+```{r porbit-dependent-vars}
 count(treated, frac_change_20) %>%
@@
 
-Regression with M-estimation estimates coefficients, $\vec{\hat{\beta}}$, that minimize standardized residuals where outliers receive less weight
-
-todo(aaron): citation
+Regression with M-estimation [@Huber1964] estimates coefficients, $\vec{\hat{\beta}}$, that minimize standardized residuals where outliers receive less weight
 
@@
 
-```{r results = "asis"}
+```{r ols-model, results = "asis"}
 #
@@
 
-```{r results = "asis"}
+```{r mestimation-model, results = "asis"}
 #
@@
 
-```{r results = "asis"}
+```{r rank-based-regression, results = "asis"}
 #
@@
 
-```{r}
+```{r residual-plot}
 resid1 = augment(lm3) %>%
@@
 
-```{r}
+```{r visualize-models}
 #
@@
 
-```{r}
+```{r visualize-models2}
 #

### 2020-07-28 draft.Rmd
cleaned up table output, fixed an error in the test we were using for pairwise comparison matrix

@@
 adjusted_alpha = 2*alpha/ (k*(k-1))
-print(sprintf("Alpha of %s leads to an adjusted alpha of %s", alpha, adjusted_alpha))
 
@@
 crit_adj = calculate_critical(sample_q, adjusted_alpha)
-crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
-print(crit_message)
+# crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
+# print(crit_message)
 
@@
   for(col in names(treat_list)){
-    m[row,col] = mw_stat(treat_list[[row]], treat_list[[col]])
+    m[row,col] = wilcox.test(
+      treat_list[[row]],
+      treat_list[[col]],
+      alternative="greater")$p.value
   }
 }
-print("pairwise statistics greater than or equal to the adjusted alpha critical value")
-print(m >= crit_adj)
+#print("pairwise statistics greater than or equal to the adjusted alpha critical value")
+comparison_matrix = as.table(m <= adjusted_alpha)
+knitr::kable(comparison_matrix, caption="Significant difference found in pairwise comparison.")
 

### 2020-07-28 draft.Rmd
seperate section 4 results
swap out Tukey HSD for Kruskal Wallis

@@
 
-We will use the Tukey Permutation HSD Test to conduct a multiple comparison test of these groups.
-The test statistic will be calculated by taking the maximum absolute value of the Mann-Whitney statistic for each pairwise comparison of the three groups.
-The p-value will be calculated with a re-sampling approach.
-We will shuffle the data between groups and recalculate the test statistic 10,000 times.
-The estimated p-value will be the percentage of test statistics greater than or equal to the observed.
+We will use the Kruskal-Wallis Test to conduct a multiple comparison test of these groups.
+The test will tell us if there is a difference in the underlying distributions for the three treatments.
+The Kruskal-Wallis Test is a rank based test, as such it is somewhat resilient to outliers.
+It relies on the following three assumptions: [@HWC]
+
+1. All the observations are mutually independent
+2. The members of the three treatments are drawn from the same population.
+3. The three distributions only differ in position parameter
+
+We are clearly comfortable with the first two assumptions.
+We are comfortable with the third assumption, because outliers aside, the we can see in the data exploration section that the three treatments are all tightly clustered around 0.
 
@@
 
-$H_a: \exists i,j \text{ s.t. } \theta_i \leq\theta_j$ and $i,j\in \{x,y,z\}$
-
-To control for type one error we will use Bonferroni's adjustment for the paired test. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins]
+$H_a:[\theta_x, \theta_y, \theta_z \text{ not all equal}]$
 
@@
 
+Additionally, we will conduct a pairwise comparison test using the Wilcoxon Rank sum test as the underlying test to identify the specific pairs that might be the source of the difference.
+
+To control for type one error we will use Bonferroni's adjustment for the paired tests. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins]
+
 ### 4.2 Results
+
+#### Fligner-Policello Results
 
@@
 
+#### Kruskal-Wallis Results
+
 ```{r Tukey-HSD-setup}
 # Helper functions
-comp_sum = function(val, t1){
-# Helper function for Mann-Whitney stat
-  full = sum(t1 < val)
-  partial = 0.5 * sum(t1 == val)
-  return(full+partial)
-}
-
-mw_stat = function(t1, t2){
-  #Mann-Whitney statistic for two treatments
-  comp_sums = mapply(comp_sum, t2, MoreArgs = list(t1=t1))
-  return(sum(comp_sums))
-}
-
-general_stat_perm= function(full_data, n_s, stat_func){
-  # stat_func should take in a list of 
-  dataset = list()
-  k = length(n_s)
-  start=1
-  end=0
-  for (i in 1:k){
-    end = end + n_s[i]
-    dataset[[i]] = full_data[start:end]
-    start = end + 1
-  }
-  return(stat_func(dataset))
-}
-
-calculate_critical = function(stat_dist, alpha){
-  # stat_dist is sorted
-  R = length(stat_dist)
-  init_crit = stat_dist[R*alpha]
-  if(sum(sample_q >= init_crit)/R == alpha){
-    return(init_crit)
-  }
-  index = sum(sample_q > init_crit)
-  return(sample_q[index])
-}
+# comp_sum = function(val, t1){
+# # Helper function for Mann-Whitney stat
+#   full = sum(t1 < val)
+#   partial = 0.5 * sum(t1 == val)
+#   return(full+partial)
+# }
+# 
+# mw_stat = function(t1, t2){
+#   #Mann-Whitney statistic for two treatments
+#   comp_sums = mapply(comp_sum, t2, MoreArgs = list(t1=t1))
+#   return(sum(comp_sums))
+# }
+# 
+# 
+# general_stat_perm= function(full_data, n_s, stat_func){
+#   # stat_func should take in a list of 
+#   dataset = list()
+#   k = length(n_s)
+#   start=1
+#   end=0
+#   for (i in 1:k){
+#     end = end + n_s[i]
+#     dataset[[i]] = full_data[start:end]
+#     start = end + 1
+#   }
+#   return(stat_func(dataset))
+# }
+# 
+# calculate_critical = function(stat_dist, alpha){
+#   # stat_dist is sorted
+#   R = length(stat_dist)
+#   init_crit = stat_dist[R*alpha]
+#   if(sum(sample_q >= init_crit)/R == alpha){
+#     return(init_crit)
+#   }
+#   index = sum(sample_q > init_crit)
+#   return(sample_q[index])
+# }
 
@@
 # Permutation Tukey HSD test
-q_star = function(dataset){
-  # Permutation HSD pg 97
-  # Use the Mann-Whitney for T
-  k = length(dataset)
-  max_t = 0
-  for (i in 1:(k-1)) {
-    for(j in (i+1):k){
-      t = abs(mw_stat(dataset[[i]], dataset[[j]]))
-      if (t > max_t){
-        max_t = t
-      }
-    }
-  }
-  return(max_t)
-}
+# q_star = function(dataset){
+#   # Permutation HSD pg 97
+#   # Use the Mann-Whitney for T
+#   k = length(dataset)
+#   max_t = 0
+#   for (i in 1:(k-1)) {
+#     for(j in (i+1):k){
+#       t = abs(mw_stat(dataset[[i]], dataset[[j]]))
+#       if (t > max_t){
+#         max_t = t
+#       }
+#     }
+#   }
+#   return(max_t)
+# }
 
@@
 
-R = 10000
-permutations = matrix(NA, ncol = N, nrow=R)
-for (i in 1:R){
-  permutations[i,] = sample(full_data)
-}
-sample_q = apply(permutations, 1, general_stat_perm, n_s, q_star)
-sample_q = sort(sample_q, decreasing = TRUE)
-
 alpha = 0.05
@@
 
-crit_alpha = calculate_critical(sample_q, alpha)
-crit_adj = calculate_critical(sample_q, adjusted_alpha)
-# crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
-# print(crit_message)
-
-q_obs = q_star(treat_list)
-obs_message = sprintf("The observed value of Q* is: %s", q_obs)
-print(obs_message)
-
-counts = sum(sample_q>= q_obs)
-p_val = counts/R
-p_message = sprintf("With a p-value of %s", p_val)
-print(p_message)
+# R = 10000
+# permutations = matrix(NA, ncol = N, nrow=R)
+# for (i in 1:R){
+#   permutations[i,] = sample(full_data)
+# }
+# sample_q = apply(permutations, 1, general_stat_perm, n_s, q_star)
+# sample_q = sort(sample_q, decreasing = TRUE)
+# 
+# 
+# 
+# crit_alpha = calculate_critical(sample_q, alpha)
+# crit_adj = calculate_critical(sample_q, adjusted_alpha)
+# # crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
+# # print(crit_message)
+# 
+# q_obs = q_star(treat_list)
+# obs_message = sprintf("The observed value of Q* is: %s", q_obs)
+# print(obs_message)
+# 
+# counts = sum(sample_q>= q_obs)
+# p_val = counts/R
+# p_message = sprintf("With a p-value of %s", p_val)
+# print(p_message)
+kw_result = kruskal.test(treat_list)
+kw_result
 
@@
 comparison_matrix = as.table(m <= adjusted_alpha)
-knitr::kable(comparison_matrix, caption="Significant difference found in pairwise comparison.")
+knitr::kable(comparison_matrix, caption="Significant difference found in pairwise comparison with Wilcoxon Test.")
 
@@
 
-A p-value of `r p_val` for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative.
+A p-value of `r kw_result$p.value` for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative.
 We conclude that there is a difference in savings between at least two of the groups.
 
-The matrix shows that the SEED accounts had better savings than the control group and the marketing groups.
+The matrix shows that the SEED accounts had better savings than the control group, but not the marketing groups.
 No other differences were significant.
-This allows us to conclude that the SEED accounts had better savings than the other two groups.
+This allows us to conclude that the SEED accounts had better savings than the control, but are not significantly more effective than the marketing groups.
+This is a contradiction to the original paper.
 

### 2020-07-28 draft.Rmd
remove commented code

@@
 
-```{r Tukey-HSD-setup}
-# Helper functions
-# comp_sum = function(val, t1){
-# # Helper function for Mann-Whitney stat
-#   full = sum(t1 < val)
-#   partial = 0.5 * sum(t1 == val)
-#   return(full+partial)
-# }
-# 
-# mw_stat = function(t1, t2){
-#   #Mann-Whitney statistic for two treatments
-#   comp_sums = mapply(comp_sum, t2, MoreArgs = list(t1=t1))
-#   return(sum(comp_sums))
-# }
-# 
-# 
-# general_stat_perm= function(full_data, n_s, stat_func){
-#   # stat_func should take in a list of 
-#   dataset = list()
-#   k = length(n_s)
-#   start=1
-#   end=0
-#   for (i in 1:k){
-#     end = end + n_s[i]
-#     dataset[[i]] = full_data[start:end]
-#     start = end + 1
-#   }
-#   return(stat_func(dataset))
-# }
-# 
-# calculate_critical = function(stat_dist, alpha){
-#   # stat_dist is sorted
-#   R = length(stat_dist)
-#   init_crit = stat_dist[R*alpha]
-#   if(sum(sample_q >= init_crit)/R == alpha){
-#     return(init_crit)
-#   }
-#   index = sum(sample_q > init_crit)
-#   return(sample_q[index])
-# }
-
-```
-
 ```{r Tukey-HSD}
@@
 
-# Permutation Tukey HSD test
-# q_star = function(dataset){
-#   # Permutation HSD pg 97
-#   # Use the Mann-Whitney for T
-#   k = length(dataset)
-#   max_t = 0
-#   for (i in 1:(k-1)) {
-#     for(j in (i+1):k){
-#       t = abs(mw_stat(dataset[[i]], dataset[[j]]))
-#       if (t > max_t){
-#         max_t = t
-#       }
-#     }
-#   }
-#   return(max_t)
-# }
-
 treat_list = list(
@@
 k = length(treat_list)
-n_s = mapply(length, treat_list)
-N = sum(n_s)
-full_data = unlist(treat_list)
 
@@
 
-# R = 10000
-# permutations = matrix(NA, ncol = N, nrow=R)
-# for (i in 1:R){
-#   permutations[i,] = sample(full_data)
-# }
-# sample_q = apply(permutations, 1, general_stat_perm, n_s, q_star)
-# sample_q = sort(sample_q, decreasing = TRUE)
-# 
-# 
-# 
-# crit_alpha = calculate_critical(sample_q, alpha)
-# crit_adj = calculate_critical(sample_q, adjusted_alpha)
-# # crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
-# # print(crit_message)
-# 
-# q_obs = q_star(treat_list)
-# obs_message = sprintf("The observed value of Q* is: %s", q_obs)
-# print(obs_message)
-# 
-# counts = sum(sample_q>= q_obs)
-# p_val = counts/R
-# p_message = sprintf("With a p-value of %s", p_val)
-# print(p_message)
 kw_result = kruskal.test(treat_list)

### 2020-07-28 draft.Rmd
add variance plot by group with outliers removed

@@
 rm(skewa, skewb)
+
+```
+
+```{r variance-by-group-quantile}
+
+skewc = treated %>%
+  group_by(group) %>%
+  filter(balchange < quantile(balchange, 0.99)) %>%
+  ggplot(aes(balchange, y = group, color = group)) +
+  geom_point(alpha=0.2) +
+  scale_x_continuous(labels = scales::comma) +
+  labs(title = "Variance by treatment having removed significant outliers",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal()
+
+skewc
+rm(skewc)
 

### 2020-07-29 draft.Rmd

--- 2020-07-28 draft.Rmd
@@
   pdf_document
-fontsize: 10pt 
+fontsize: 12pt 
 editor_options: 
@@
 library(Rfit) # rank-based regression
-library(patchwork)
-library(broom)
-library(sandwich)
-library(lmtest)
+library(patchwork) # for combining ggplot2s
+library(broom) # for tidying regression output
+library(sandwich) # for HC1 robust standard errors
+library(lmtest) # for HC1 robust standard errors
 library(NSM3)
+library(knitr) # for tables
 
@@
 
-The key outcomes of interest for this reanalysis, the change in balance after six months and the change in balance after twelve months, are both highly right skewed.
+The key outcomes of interest for this reanalysis, the change in balance after six months and the change in balance after twelve months, are both highly right skewed as demonstrated in \textit{figure 1}.
 
@@
                      labels = scales::comma) +
-  labs(title = "The Dependent Variables Are Highly Right Skewed",
+  labs(title = "Figure 1: The Dependent Variables Are Highly Right Skewed",
        subtitle = "Six Month Change in Balance",
@@
 
-Here is the same information as a kernel density estimate (KDE).
+\textit{Figure 2} displays the same data as \textit{figure 1} as a kernel density estimate (KDE).
 
@@
   scale_y_continuous(limits = c(0, 0.004)) +
-  labs(title = "The Dependent Variables Are Highly Right Skewed",
+  labs(title = "Figure 2: The Dependent Variables Are Highly Right Skewed",
        subtitle = "Six Month Change in Balance",
@@
 
-The right skew is present in the treatment and control groups, but it most pronounced in the commit-savings treatment group after twelve months.
+The right skew is present in the treatment and control groups, but it most pronounced in the commit-savings treatment group after twelve months as demonstrated in \textit{figure 3}.
 
@@
   scale_x_continuous(labels = scales::comma) +
-  labs(title = "The Dependent Variables Are Highly Right Skewed",
+  labs(title = "Figure 3: The Dependent Variables Are Highly Right Skewed",
        subtitle = "Six Month Change in Balance",
@@
 rm(skewa, skewb)
+
+```
+
+```{r variance-by-group-quantile}
+
+skewc = treated %>%
+  group_by(group) %>%
+  filter(balchange < quantile(balchange, 0.99)) %>%
+  ggplot(aes(balchange, y = group, color = group)) +
+  geom_point(alpha=0.2) +
+  scale_x_continuous(labels = scales::comma) +
+  labs(title = "Figure 4: Variance by treatment having removed significant outliers",
+       x = "Change in balance (Philippine Peso)",
+       y = NULL) +  
+  theme_minimal()
+
+skewc
+rm(skewc)
 
@@
 ```{r wilcox-paired-test}
-wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)
+wilcox_test = wilcox.test(seed_accounts$totbal,
+                          seed_accounts$newtotbal,
+                          alternative = "greater", 
+                          paired = TRUE)
+
+tibble(
+  Metric = c("Test Statistic", "P-Value"),
+  Value = c(wilcox_test$statistic, wilcox_test$p.value)
+) %>%
+  kable(caption = "Wilcoxon Signed-Rank Test Results")
 
@@
 ```{r 2-sample}
+#
+# Fligner-Policello test
+#
 x = list(nonseed$balchange, seed_accounts$balchange)
 fp_result = pFligPoli(x, method="Monte Carlo")
-fp_result
+
+tibble(
+  Metric = c("Fligner-Policello U Statistic", "two-sided p-value"),
+  Value = c(fp_result$obs.stat, fp_result$two.sided)
+) %>%
+  kable(caption = "Fligner-Policello Test Results")
+
 ```
+
+Test conducted with `r fp_result$m` X values, `r fp_result$n` Y values, and 10000 iterations.
 
@@
 
-```{r Tukey-HSD}
+```{r kruskal-wallis}
+#
+# Kruskal-Wallis test
+#
 
 seed_balchange = seed_accounts$balchange
+
 marketing_balchange = treated %>% 
@@
   pull(balchange)
+
 control_balchange = treated %>% 
@@
 kw_result = kruskal.test(treat_list)
-kw_result
+
+tibble(
+  Metric = c("Chi-Squared", "Degrees Freedom", "P-Value"),
+  Value = c(kw_result$statistic, kw_result$parameter, kw_result$p.value)
+) %>%
+  kable(caption = "Kruskal-Wallis Test Results")
 
@@
 }
-#print("pairwise statistics greater than or equal to the adjusted alpha critical value")
-comparison_matrix = as.table(m <= adjusted_alpha)
-knitr::kable(comparison_matrix, caption="Significant difference found in pairwise comparison with Wilcoxon Test.")
+
+as.table(m <= adjusted_alpha) %>%
+  kable(caption = "Significant difference found in\n
+        pairwise comparison with Wilcoxon Test.")
 
@@
 
-The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months as demonstrated in [todo(aaron): add plot number from above].
+The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months as demonstrated in \textit{figure 2}.
 Accordingly, the dependent variable is not approximately normally distributed and the error term of their estimated models is not approximately normally distributed.
 
-[todo(aaron): add plot number from above] The SEED treatment, the marketing control, and the full control all have outliers.
+As \textit{figure 3} demonstrated, the SEED treatment, the marketing control, and the full control all have outliers.
 Though the SEED treatment's outliers are distinct for the change in twelve month balance.
@@
               values_from = n) %>%
-  knitr::kable(caption = "Change in Balance After Twelve Months")
+  kable(caption = "Change in Balance After Twelve Months")
 
@@
               values_from = n) %>%
-  knitr::kable(caption = "Change in Balance After Twelve Months by Treatment Group")
+  kable(caption = "Change in Balance After Twelve Months by Treatment Group")
 
@@
          `<20% Increase` = `0`) %>%
-  knitr::kable(caption = "20+% Change in Balance After Twelve Months")
+  kable(caption = "20+% Change in Balance After Twelve Months")
 
@@
          `<20% Increase` = `0`) %>%  
-  knitr::kable(caption = "20+% Change in Balance After Twelve Months")
+  kable(caption = "20+% Change in Balance After Twelve Months")
 
@@
 We estimate identical specifications to [@Ashraf2006] using M-estimation.
-Column (1) shows the change in balance after six months including all observations.
+Column (1) in \textit{table 10} shows the change in balance after six months including all observations.
 The coefficients estimate the additional savings of the corresponding treatment over the control group.
@@
 # column 1
-m_model1 = rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = six_months)
+m_model1 = rlm(balchange ~ treatment + marketing, 
+               method = "M", 
+               psi = psi.bisquare, 
+               data = six_months)
 
 # column 2
-m_model2 = rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
+m_model2 = rlm(balchange ~ treatment, 
+               method = "M", 
+               psi = psi.bisquare, 
                data = filter(six_months, group %in% c("M", "T")))
@@
 # column 3
-m_model3 = rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = treated)
+m_model3 = rlm(balchange ~ treatment + marketing,
+               method = "M", 
+               psi = psi.bisquare, 
+               data = treated)
 
 # column 4
-m_model4 = rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
+m_model4 = rlm(balchange ~ treatment, 
+               method = "M", 
+               psi = psi.bisquare, 
                data = filter(treated, group %in% c("M", "T")))
@@
 We estimate identical specifications to [@Ashraf2006] using robust and rank-based regressions.
-Column (1) shows the change in balance after six months including all observations.
+Column (1) in \textit{table 11} shows the change in balance after six months including all observations.
 The coefficients estimate the additional savings of the corresponding treatment over the control group.
@@
 # column 1
-rank_model1 = rfit(balchange ~ treatment + marketing, data = six_months)
+rank_model1 = rfit(balchange ~ treatment + marketing, 
+                   data = six_months)
 
@@
 # column 3
-rank_model3 = rfit(balchange ~ treatment + marketing, data = treated)
+rank_model3 = rfit(balchange ~ treatment + marketing, 
+                   data = treated)
 
@@
   m_model1, m_model2, m_model3, m_model4,
-  coef = list(coef(rank_model1), coef(rank_model2), coef(rank_model3), coef(rank_model4)),
+  coef = list(coef(rank_model1), 
+              coef(rank_model2), 
+              coef(rank_model3), 
+              coef(rank_model4)),
   se = list(coef(summary(rank_model1))[, 2],
@@
 The models estimated with OLS have residuals that are highly skewed.
-The following QQ plots demonstrate that many of the residuals are approximately normally distributed, as they fall on the diagonal line.
+\textit{Figure 5} displays QQ plots that demonstrate that many of the residuals are approximately normally distributed, as they fall on the diagonal line.
 However, the residuals dramatically depart the line at higher values.
@@
   theme_minimal() +
-  labs(title = "The Estimated Model has Significant Outliers",
+  labs(title = "Figure 5: The Estimated Model has Significant Outliers",
        subtitle = "QQ Plot for OLS (3)")
@@
 
-The following data  compares the estimated coefficients and confidence intervals from column (3) for all three model types.
+\textit{Figure 6} compares the estimated coefficients and confidence intervals from column (3) for all three model types.
 
@@
          conf.high = estimate + qnorm(0.025) * std.error) %>%
-  mutate(model = factor(model, levels = c("Rank-Based\nModel", "M Model", "OLS Model"))) %>%
+  mutate(model = factor(model, 
+                        levels = c("Rank-Based\nModel", "M Model", "OLS Model"))) %>%
   ggplot(aes(x = estimate, 
@@
   facet_wrap(~term, scales = "free_x") +
-  labs(title = "Model Choice Affects Estimated Coefficients",
+  labs(title = "Figure 6: Model Choice Affects Estimated Coefficients",
        x = "Estimated Beta and 95% Confidence Interval",
@@
 
-The following data visualization compares the estimated coefficients and confidence intervals from column (4) for all three model types.
+\textit{Figure 7} compares the estimated coefficients and confidence intervals from column (4) for all three model types.
 
@@
   facet_wrap(~term, scales = "free_x") +
-  labs(title = "Model Choice Affects Estimated Coefficients",
+  labs(title = "Figure 7: Model Choice Affects Estimated Coefficients",
        x = "Estimated Beta and 95% Confidence Interval",
@@
 
+\newpage
+
 ## References

### 2020-07-29 draft.Rmd
Some final tweaks and a draft of the conclusion

@@
 We are clearly comfortable with the first two assumptions.
-We are comfortable with the third assumption, because outliers aside, the we can see in the data exploration section that the three treatments are all tightly clustered around 0.
+We are comfortable with the third assumption, because outliers aside, the we can see in Figure 4 that three treatments have similar spreads after the significant outliers are removed.
 
@@
 
-To control for type one error we will use Bonferroni's adjustment for the paired tests. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins]
+If we were doing a pairwise comparison test to determine the existance of a difference, we would use Bonferroni's adjustment for the paired tests to control for type one error.
+Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins].
+However, we will only be using the pairwise comparison after the k-sample Kruskal-Wallis test, so we do not need to be concerned with it here.
 
@@
 
-as.table(m <= adjusted_alpha) %>%
-  kable(caption = "Significant difference found in\n
+as.table(m) %>%
+  kable(caption = "P-value for paired onesided Wilcoxon test")
+
+as.table(m <= alpha) %>%
+  kable(caption = "Significant difference found in
         pairwise comparison with Wilcoxon Test.")
@@
 
-A p-value of `r kw_result$p.value` for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative.
+A p-value of `r kw_result$p.value` for the Kruskal-Wallis Test leads us to reject the null hypothesis in favor of the alternative.
 We conclude that there is a difference in savings between at least two of the groups.
 
-The matrix shows that the SEED accounts had better savings than the control group, but not the marketing groups.
-No other differences were significant.
-This allows us to conclude that the SEED accounts had better savings than the control, but are not significantly more effective than the marketing groups.
-This is a contradiction to the original paper.
+Tables 4 and 5 show a significant difference in three one-sided comparisons tests.
+We can reasonably conclude that the SEED accounts perform better than the control groups and the marketing treatment.
+However, it is worth noting that if we used the Bonferroni adjustment for alpha, we would only mark a significant difference between the seed and control groups.
 
@@
 
-We estimate identical specifications to [@Ashraf2006] using robust and rank-based regressions.
-Column (1) in \textit{table 11} shows the change in balance after six months including all observations.
-The coefficients estimate the additional savings of the corresponding treatment over the control group.
-Column (2) shows the change in balance after six months using only the commitment savings group and the marketing group.
-Column (3) is similar to column (1), only it uses the twelve month change in balance.
-Likewise, column (4) is similar to column (2), only it uses the twelve month change in balance.
-
 ```{r rank-based-regression, results = "asis"}
@@
 ```
+
+We estimate identical specifications to [@Ashraf2006] using robust and rank-based regressions.
+Column (1) in \textit{table 11} and \text{table 12} shows the change in balance after six months including all observations.
+The coefficients estimate the additional savings of the corresponding treatment over the control group.
+Column (2) shows the change in balance after six months using only the commitment savings group and the marketing group.
+Column (3) is similar to column (1), only it uses the twelve month change in balance.
+Likewise, column (4) is similar to column (2), only it uses the twelve month change in balance.
 
@@
 
+In most cases our findings are aligned with the original paper.
+In section 3 we conclude that the SEED accounts are effective savings mechanisms, agreeing with the original authors.
+In section 4 we conclude that there is a difference between the three different treatments, but make a note that depending on the significance level employed we have reason to doubt that there is a difference between the marketing treatment and the SEED accounts.
+The tests concluded a difference, but further study is warranted.
+In section 5 we used different regression techniques from the original paper, as the authors had done a good bit of massaging to make OLS work.
+While the non parametric methods did conclude statistical siginificance of the SEED treatments over the marketing treatments, the coefficients determined by the methods were significantly lower.
+Leading us to conclude that while there is a statistically significant effect of the SEED accounts on savings compared to the marketing treatment, there is not necessarily a practically significant effect.
+
+Overall, we conclude that the SEED accounts are effective saving mechanisms, with some marginal benefits over marketing treatments.
+However, like the authors of the original paper, we also recommend further study into the true effectiveness of the accounts, and how large the difference is between them and other potential marketing strategies.
+
 \newpage

### 2020-07-29 draft.Rmd
FIx typos and clean up narrative

@@
 [@Ashraf2006] implemented a randomized control trial (RCT) to 1.
-see if individuals offered accounts opens accounts, and if so, what characteristics are associated with opening an account and 2.
+see if individuals offered accounts open accounts, and if so, what characteristics are associated with opening an account and 2.
 if individuals save more as a result of opening an account.
@@
 The authors partnered with a rural bank in Mindanao, Philippines called Green Bank of Caraga.
-After two rounds of randomization, they ended up with a survey size of 1,777 people who completed a baseline household survey.
+After two rounds of randomization, they ended up with a sample size of 1,777 people who completed a baseline household survey.
 They then randomly assigned the individuals to the commitment treatment (T), marketing-treatment (M), and control (C) groups.
@@
 We conclude using paired comparisons that customers who had SEED accounts saw an increase in savings over the duration of the trial.
-We conclude using Tukey Permutation Honest Significant Difference tests that SEED accounts had more savings than the other two groups.
+We conclude using Kruskal-Wallis tests that SEED accounts had more savings than the other two groups.
 Finally, using M-Estimation and rank-based and robust regression we find that SEED accounts had more savings than the other two groups; however, we find much smaller effect sizes than [@Ashraf2006].
@@
 
-The right skew is present in the treatment and control groups, but it most pronounced in the commit-savings treatment group after twelve months as demonstrated in \textit{figure 3}.
+The right skew is present in the treatment and control groups, but is most pronounced in the commitment-savings treatment group after twelve months as demonstrated in \textit{figure 3}.
 
@@
 
-As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternate hypothesis.
+As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternative hypothesis.
 We conclude that customers who had SEED accounts saw an increase in savings over the duration of the trial.
@@
 
-In addition to testing whether or not the SEED accounts are more effective savings than a control group, we also want to confirm that the SEED accounts are more effective than just the marketing that comes with them.
+In addition to testing whether or not the SEED accounts are more effective for savings than a control group, we also want to test that the SEED accounts are more effective than just the marketing that comes with them.
 To do this we divide the customers into three groups.
@@
 We are clearly comfortable with the first two assumptions.
-We are comfortable with the third assumption, because outliers aside, the we can see in Figure 4 that three treatments have similar spreads after the significant outliers are removed.
+We are comfortable with the third assumption, because outliers aside, we can see in \textit{Figure 4} that three treatments have similar spreads after the significant outliers are removed.
 
@@
 
-A p-value of `r fp_result$p.val` for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternate.
+A p-value of `r fp_result$p.val` for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternative.
 We conclude that the median savings for SEED accounts is higher an for non-SEED accounts.
@@
 The dependent variable, change in savings account balance, is highly right-skewed after six months and twelve months as demonstrated in \textit{figure 2}.
-Accordingly, the dependent variable is not approximately normally distributed and the error term of their estimated models is not approximately normally distributed.
+Accordingly, the dependent variable is not approximately normally distributed and the error terms of their estimated models are not approximately normally distributed.
 
@@
 [@Ashraf2006] estimate their models on the untransformed data and find only modest evidence for a statistically significant intent-to-treat (ITT) effect for the commitment savings accounts using ordinary least squares regression (OLS).
-Furthermore, they found that the differential effect of being offered the commitment savings product beyond being offered only a marketing treatment was indistinguishable from zero.
+Furthermore, they find that the differential effect of being offered the commitment savings product beyond being offered only a marketing treatment was indistinguishable from zero.
 
@@
 ### 5.2 Results
+
+All results in this section are in Philippine Pesos. About 50 Philippine Pesos converted to one U.S. Dollar when the data were collected.
 
@@
 
-In most cases our findings are aligned with the original paper.
+In most cases, the conclusions of our tests aligned with the original paper.
 In section 3 we conclude that the SEED accounts are effective savings mechanisms, agreeing with the original authors.
@@
 In section 5 we used different regression techniques from the original paper, as the authors had done a good bit of massaging to make OLS work.
-While the non parametric methods did conclude statistical siginificance of the SEED treatments over the marketing treatments, the coefficients determined by the methods were significantly lower.
+While the nonparametric methods did conclude statistical significance of the SEED treatments over the marketing treatments, the coefficients determined by the methods were significantly lower.
 Leading us to conclude that while there is a statistically significant effect of the SEED accounts on savings compared to the marketing treatment, there is not necessarily a practically significant effect.
 
-Overall, we conclude that the SEED accounts are effective saving mechanisms, with some marginal benefits over marketing treatments.
+Overall, we conclude that the SEED accounts are modestly effective saving mechanisms, with some marginal benefits over marketing treatments.
 However, like the authors of the original paper, we also recommend further study into the true effectiveness of the accounts, and how large the difference is between them and other potential marketing strategies.

### 2020-07-29 draft.Rmd

@@
 We conclude using paired comparisons that customers who had SEED accounts saw an increase in savings over the duration of the trial.
-We conclude using Kruskal-Wallis tests that SEED accounts had more savings than the other two groups.
+We conclude using Kruskal-Wallis tests that there exists a difference within the three groups.
 Finally, using M-Estimation and rank-based and robust regression we find that SEED accounts had more savings than the other two groups; however, we find much smaller effect sizes than [@Ashraf2006].
@@
 
-If we were doing a pairwise comparison test to determine the existance of a difference, we would use Bonferroni's adjustment for the paired tests to control for type one error.
-Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins].
-However, we will only be using the pairwise comparison after the k-sample Kruskal-Wallis test, so we do not need to be concerned with it here.
+To control for type one error we will use Bonferroni's adjustment for the paired tests. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins].
 
@@
 
-as.table(m <= alpha) %>%
+as.table(m <= adjusted_alpha) %>%
   kable(caption = "Significant difference found in
@@
 
-Tables 4 and 5 show a significant difference in three one-sided comparisons tests.
-We can reasonably conclude that the SEED accounts perform better than the control groups and the marketing treatment.
-However, it is worth noting that if we used the Bonferroni adjustment for alpha, we would only mark a significant difference between the seed and control groups.
+Tables 4 and 5 show a significant difference in the SEED accounts versus the control group.
+Therefore, we can reasonably conclude that the SEED accounts perform better than the control group.
+However, it is worth noting that under the Bonferroni adjustment for alpha, we do not mark a significant difference between marketing and control, or SEED and marketing.
 
@@
 In section 3 we conclude that the SEED accounts are effective savings mechanisms, agreeing with the original authors.
-In section 4 we conclude that there is a difference between the three different treatments, but make a note that depending on the significance level employed we have reason to doubt that there is a difference between the marketing treatment and the SEED accounts.
-The tests concluded a difference, but further study is warranted.
+In section 4 we conclude that there is a difference within the three treatments, but we make a note that we could not determine a significant difference between the SEED accounts and the marketing group.
+The tests concluded a difference overall, but further study is warranted.
 In section 5 we used different regression techniques from the original paper, as the authors had done a good bit of massaging to make OLS work.
